---
title: "3 station compare"
output: html_document
date: "2024-05-23"
---

<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>


```{r, echo=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R/station compare/read_data.R")  ## read data
source("../R/station compare/plot_90th.R")  ## clean data for 90th line plot 
source("../R/station compare/scatter_2_station.R") ## plot for 2 station compare for all the station 

source("../R/station compare/read_data_3day_hw.R")  ## read data
source("../R/station compare/read_data_5day_hw.R")  ## read data
source("../R/station compare/line_segment_plot.R")  ## plot for 3 station

```


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>ALL diff station 90th compare </b>
</h3>
<div style="display:none;">
```{r, echo=FALSE,message=FALSE}
three_stations_90th
```
</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>compare 90th percentile of original YVR and YVR with base period 1961-1990</b>
</h3>
<div style="display:none;"> 
```{r, echo=FALSE,message=FALSE}
two_stations_90th_yvr_30
```

## read data 
```{r, echo=FALSE,message=FALSE}
# Define file paths
file_paths <- c("../output/Kamloops_heatmap_data.csv",       # Adding this file
                "../output/Prince_George_heatmap_data.csv",  # Adding this file
                "../output/YVR_heatmap_data.csv")             # Adding this file

# Define the columns needed


# Define the columns needed
needed_columns <- c("Year","DayOfYear","Max_Temp_Year","Percentile_90","Station")

# Function to read and select necessary columns
read_and_select <- function(file_path) {
  read.csv(file_path) %>%
    select(all_of(needed_columns))
}

# Read and combine all datasets
df_heatmap_all <- map_dfr(file_paths, read_and_select)


```





</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>data clean results</b>
</h3>
<div style="display:none;">    

```{r, echo=FALSE}
# Display the first few rows of the combined data
# head(df_heatmap_all)
# 
# tail(df_heatmap_all)

library(dplyr)
library(lubridate)

# Assuming your data frame is named df_heatmap_all

# Convert DayOfYear to Date
df_heatmap_all <- df_heatmap_all %>%
  mutate(Date = as.Date(paste(Year, DayOfYear, sep = "-"), format = "%Y-%m-%d"))

# Filter for dates between April 1st and October 31st
filtered_heatmap_all <- df_heatmap_all %>%
  filter(month(Date) >= 4 & month(Date) <= 10)

# Remove the Date column if needed
filtered_heatmap_all <- filtered_heatmap_all %>%
  select(-Date)

# Display the filtered data

filtered_heatmap_all <- filtered_heatmap_all %>% filter(!is.na(Max_Temp_Year))



```



```{r, echo=FALSE,message=FALSE}
# Filter the data frame to include only rows with negative Max_Temp_Year values
negative_temps <- filtered_heatmap_all %>%
  filter(Max_Temp_Year < 0)

# Display the rows with negative temperatures
#negative_temps


dfdebug <- df_heatmap_all %>%
  filter(Station == "Kamloops" | Station == "Prince_George")

duplicate_temps <- dfdebug %>%
  group_by(Year, DayOfYear, Max_Temp_Year) %>%
  filter(n_distinct(Station) > 1) %>%
  ungroup()

# Sort the filtered dataframe
sorted_df <- duplicate_temps %>%
  arrange(Year, DayOfYear, Max_Temp_Year, Station)

# Display the results
#print(sorted_df)


# Load necessary library
library(dplyr)

# Assuming df_heatmap_all is your dataframe
df_count_sorted_df <- sorted_df %>%
  group_by(Year) %>%
  summarise(Count = n())

# View the result
#print(df_count_sorted_df)

```

</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>PLOT</b>
</h1>
<div style="display:none;">    

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>scatter plot between 2 stations</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE}
# library(ggplot2)
# library(dplyr)
# 
# # Ensure your filtered data frame is named filtered_heatmap_all
# 
# # List of unique stations
# stations <- unique(filtered_heatmap_all$Station)
# 
# # Generate scatter plots for each pair of stations
# for (i in 1:(length(stations)-1)) {
#   for (j in (i+1):length(stations)) {
#     station1 <- stations[i]
#     station2 <- stations[j]
#     
#     # Filter data for the two stations
#     df_station1 <- filtered_heatmap_all %>% filter(Station == station1)
#     df_station2 <- filtered_heatmap_all %>% filter(Station == station2)
#     
#     # Merge data on Date
#     df_merged <- merge(df_station1, df_station2, by = c("Year", "DayOfYear"), suffixes = c("_1", "_2"))
#     
#     # Create scatter plot
#     plot <- ggplot(df_merged, aes(x = Max_Temp_Year_1, y = Max_Temp_Year_2)) +
#       geom_point() +
#       labs(
#         title = paste("Scatter Plot of Max Temperature:", station1, "vs", station2),
#         x = paste("Max Temperature (", station1, ")", sep = ""),
#         y = paste("Max Temperature (", station2, ")", sep = "")
#       ) +
#       theme_minimal()
#     
#     # Print the plot
#     print(plot)
#   }
# }

```


```{r, echo=FALSE,message=FALSE}

dftop20 <- generate_extreme_temp_scatter_plots(filtered_heatmap_all, 1:19)
#dftop20
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Display the results</b>
</h4>
<div style="display:none;"> 
```{r, echo=FALSE,message=FALSE}
# Assuming label_dataframes is already defined
results <- analyze_extrem_scatter(dftop20)

# Display the results
print(results$unique_year_counts)
print(results$unique_yearmonth_counts)



```


```{r, echo=FALSE,message=FALSE}

df_top20_35 <- generate_extreme_temp_scatter_plots(filtered_heatmap_all, 19:35)


```
```{r, echo=FALSE,message=FALSE}
# Assuming label_dataframes is already defined
results <- analyze_extrem_scatter(df_top20_35)

# Display the results
print(results$unique_year_counts)
print(results$unique_yearmonth_counts)



```
</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>line segment plot</b>
</h1>
<div style="display:none;"> 

## line segment 3 day
```{r, echo=FALSE,message=FALSE}




line_segment_plot(df_line_seg_3day, station_only = c("YVR", "Prince_George","Kamloops"))
  
```


## line segment 5 day
```{r, echo=FALSE,message=FALSE}

df_filtered_line_seg_5d <- df_line_seg_5day[ (df_line_seg_5day$Heatwave) == "Heatwave",]
#df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]

# Check for and remove any remaining NA values in the station column
df_filtered_line_seg_5d <- df_filtered_line_seg_5d %>%
  filter(!is.na(station))
line_segment_plot(df_filtered_line_seg_5d, station_only = c("YVR", "Prince_George","Kamloops"))

```





## line segment 2 data yvr
```{r, echo=FALSE,message=FALSE}

df_filtered_line_seg_3d <- df_line_seg_3day[ (df_line_seg_3day$Heatwave) == "Heatwave",]
#df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]

# Check for and remove any remaining NA values in the station column
df_filtered_line_seg_3d <- df_filtered_line_seg_3d %>%
  filter(!is.na(station))
line_segment_plot(df_filtered_line_seg_3d,station_only = c("YVR", "YVR_era5"))
  
```

## line segment 5 day yvr compare
```{r, echo=FALSE,message=FALSE}

df_filtered_line_seg_5d <- df_line_seg_5day[ (df_line_seg_5day$Heatwave) == "Heatwave",]
#df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]

# Check for and remove any remaining NA values in the station column
df_filtered_line_seg_5d <- df_filtered_line_seg_5d %>%
  filter(!is.na(station))
line_segment_plot(df_filtered_line_seg_5d, station_only = c("YVR", "YVR_era5"))

```





## line segment 3 day
```{r, echo=FALSE,message=FALSE}

df_filtered_line_seg_3d <- df_line_seg_3day[ (df_line_seg_3day$Heatwave) == "Heatwave",]
#df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]

# Check for and remove any remaining NA values in the station column
df_filtered_line_seg_3d <- df_filtered_line_seg_3d %>%
  filter(!is.na(station))
line_segment_plot(df_filtered_line_seg_3d, station_only = c("YVR_era5", "Prince_George","Kamloops"))
  
```


## line segment 5 day
```{r, echo=FALSE,message=FALSE}

df_filtered_line_seg_5d <- df_line_seg_5day[ (df_line_seg_5day$Heatwave) == "Heatwave",]
#df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]

# Check for and remove any remaining NA values in the station column
df_filtered_line_seg_5d <- df_filtered_line_seg_5d %>%
  filter(!is.na(station))
line_segment_plot(df_filtered_line_seg_5d, station_only = c("YVR_era5", "Prince_George","Kamloops"))

```