---
title: "3 station compare"
output: html_document
author: "alex lin "
date: "`r format(Sys.Date(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: 72
---


```{=html}
<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>
```


```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R/station compare/read_data.R")  ## read data
source("../R/station compare/plot_90th.R")  ## clean data for 90th line plot 
source("../R/station compare/scatter_2_station.R") ## plot for 2 station compare for all the station 
source("../R/station compare/read_data_3day_hw.R")  ## read data
source("../R/station compare/read_data_5day_hw.R")  ## read data
source("../R/station compare/line_segment_plot.R")  ## plot for 3 station


source("../R/station compare/EHF_summary.R")  ##EHF compare

```

<h1 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Part 1 90th percentile</b>

</h1>

::: {style="display:none;"}
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b> 1.1 ALL station 90th compare</b>

</h3>

::: {style="display:none;"}
```{r, echo=FALSE,message=FALSE}

three_stations_90th
three_stations_90th_filter
```
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>1.2 different YVR data</b>

</h3>

::: {style="display:none;"}
## compare 90th percentile of original YVR and YVR with base period 1961-1990

```{r, echo=FALSE,message=FALSE}
two_stations_90th_yvr_30
```
:::

<h1 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Part 2 scatter plot</b>

</h1>

::: {style="display:none;"}
```{r, echo=FALSE,message=FALSE}
# Define file paths
file_paths <- c("../output/Kamloops_heatmap_data.csv",       # Adding this file
                "../output/Prince_George_heatmap_data.csv",  # Adding this file
                "../output/YVR_heatmap_data.csv",
                "../output/Kelowna_heatmap_data.csv",
                "../output/era5_YVR_heatmap_data.csv",
                "../output/Abbotsford_heatmap_data.csv",
                "../output/Penticton_heatmap_data.csv",
                "../output/FortNelson_heatmap_data.csv")             # Adding this file

# Define the columns needed


# Define the columns needed
needed_columns <- c("Year","DayOfYear","Max_Temp_Year","Percentile_90","Station")

# Function to read and select necessary columns
read_and_select <- function(file_path) {
  read.csv(file_path) %>%
    select(all_of(needed_columns))
}

# Read and combine all datasets
df_heatmap_all <- map_dfr(file_paths, read_and_select)
unique(df_heatmap_all$Station)

```

```{r, echo=FALSE}
# Display the first few rows of the combined data
# head(df_heatmap_all)
# 
# tail(df_heatmap_all)

library(dplyr)
library(lubridate)

# Assuming your data frame is named df_heatmap_all

# Convert DayOfYear to Date
df_heatmap_all <- df_heatmap_all %>%
  mutate(Date = as.Date(paste(Year, DayOfYear, sep = "-"), format = "%Y-%m-%d"))

# Filter for dates between April 1st and October 31st
filtered_heatmap_all <- df_heatmap_all %>%
  filter(month(Date) >= 4 & month(Date) <= 10)

# Remove the Date column if needed
filtered_heatmap_all <- filtered_heatmap_all %>%
  select(-Date)

# Display the filtered data

filtered_heatmap_all <- filtered_heatmap_all %>% filter(!is.na(Max_Temp_Year))



```

```{r, echo=FALSE,message=FALSE}
# Filter the data frame to include only rows with negative Max_Temp_Year values
negative_temps <- filtered_heatmap_all %>%
  filter(Max_Temp_Year < 0)

# Display the rows with negative temperatures
#negative_temps


dfdebug <- df_heatmap_all %>%
  filter(Station == "Kamloops" | Station == "Prince_George")

duplicate_temps <- dfdebug %>%
  group_by(Year, DayOfYear, Max_Temp_Year) %>%
  filter(n_distinct(Station) > 1) %>%
  ungroup()

# Sort the filtered dataframe
sorted_df <- duplicate_temps %>%
  arrange(Year, DayOfYear, Max_Temp_Year, Station)

# Display the results
#print(sorted_df)


# Load necessary library
library(dplyr)

# Assuming df_heatmap_all is your dataframe
df_count_sorted_df <- sorted_df %>%
  group_by(Year) %>%
  summarise(Count = n())

# View the result
#print(df_count_sorted_df)

```
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>2.1 TOP 20 scatter plot between 2 stations</b>

</h3>

::: {style="display:none;"}
```{r, echo=FALSE,message=FALSE}
# library(ggplot2)
# library(dplyr)
# 
# # Ensure your filtered data frame is named filtered_heatmap_all
# 
# # List of unique stations
# stations <- unique(filtered_heatmap_all$Station)
# 
# # Generate scatter plots for each pair of stations
# for (i in 1:(length(stations)-1)) {
#   for (j in (i+1):length(stations)) {
#     station1 <- stations[i]
#     station2 <- stations[j]
#     
#     # Filter data for the two stations
#     df_station1 <- filtered_heatmap_all %>% filter(Station == station1)
#     df_station2 <- filtered_heatmap_all %>% filter(Station == station2)
#     
#     # Merge data on Date
#     df_merged <- merge(df_station1, df_station2, by = c("Year", "DayOfYear"), suffixes = c("_1", "_2"))
#     
#     # Create scatter plot
#     plot <- ggplot(df_merged, aes(x = Max_Temp_Year_1, y = Max_Temp_Year_2)) +
#       geom_point() +
#       labs(
#         title = paste("Scatter Plot of Max Temperature:", station1, "vs", station2),
#         x = paste("Max Temperature (", station1, ")", sep = ""),
#         y = paste("Max Temperature (", station2, ")", sep = "")
#       ) +
#       theme_minimal()
#     
#     # Print the plot
#     print(plot)
#   }
# }

```

```{r, echo=FALSE,message=FALSE}
dftop20 <- generate_extreme_temp_scatter_plots(filtered_heatmap_all, 1:19)
print_plot(dftop20,"FortNelson","Prince_George")
print_plot(dftop20,"FortNelson","YVR")
print_plot(dftop20,"FortNelson","Abbotsford")
print_plot(dftop20,"FortNelson","Penticton")
print_plot(dftop20,"FortNelson","Kamloops")
print_plot(dftop20,"FortNelson","Kelowna")
# print_plot(dftop20,"Abbotsford","Penticton")
# print_plot(dftop20, "Kamloops", "Prince_George")
# print_plot(dftop20, "Prince_George", "Kamloops")



```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Display the color point in bar</b>

</h4>

::: {style="display:none;"}
```{r, echo=FALSE,message=FALSE}
# Assuming label_dataframes is already defined
#results <- analyze_extrem_scatter(dftop20)

# Display the results
#print(results$unique_year_counts)
#print(results$unique_yearmonth_counts)



```
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>2.2 TOP 20-35 scatter plot between 2 stations</b>

</h3>

::: {style="display:none;"}
```{r, echo=FALSE,message=FALSE}

df_top20_35 <- generate_extreme_temp_scatter_plots(filtered_heatmap_all, 19:35)
print_plot(df_top20_35,"FortNelson","Prince_George")
print_plot(df_top20_35,"FortNelson","YVR")
print_plot(df_top20_35,"FortNelson","Abbotsford")

```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Display the color point in bar</b>

</h4>

::: {style="display:none;"}
```{r, echo=FALSE,message=FALSE}
# Assuming label_dataframes is already defined
#results <- analyze_extrem_scatter(df_top20_35)

# Display the results
# print(results$unique_year_counts)
# print(results$unique_yearmonth_counts)



```
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b> 2.3 correlation between scatter plot of YVR_era5 vs YVR temp
station.</b>

</h3>

::: {style="display:none;"}
Fit a Linear Model Generate 95% Prediction Intervals as reference lines

```{r, echo=FALSE,message=FALSE}

dftop20_yvr <- generate_scatter_plots_for_yvr_diff_data(filtered_heatmap_all, 1:19)
#dftop20
```
:::

<h1 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Part 3: line segment plot</b>

</h1>

::: {style="display:none;"}
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>3.1 line segment for 7 temp station, 3 day HW</b>


</h3>

::: {style="display:none;"}
YVR: 1937-2024

Prince_George: 1940-2024

FortNelson: 1937-2024

Kelowna: 1899-2024

Abbotsford: 1935-2024

Kamloops: 1939-2024

Penticton: 1941-2024




#### line segment 3 day

```{r, echo=FALSE,message=FALSE}




#line_segment_plot(df_line_seg_3day, station_only = c("YVR", "Prince_George","Kamloops","Kelowna"))
#+ geom_hline(aes(yintercept = as.numeric(Year)), color = "grey", linetype = "solid", alpha = 0.5)

print(unique(df_line_seg_3day$station))
# Define the colors for specific stations
station_colors <- c("Kamloops" = "red", "Prince_George" = "green", "YVR" = "blue", 'FortNelson'='#D2B48C',
                    "Kelowna" = '#FFD700', 'Penticton' = '#FF00FF', 'Abbotsford' = '#696969')

df_station_filter<- line_segment_data_prepare(df_line_seg_3day, station_only = c("YVR", "Prince_George","Kamloops","Kelowna","Abbotsford","Penticton","FortNelson"))
year_ranges <- create_year_ranges(1941, 2024, 5)
hline_data <- generate_temperature_plots("3 days long",df_station_filter, year_ranges, station_colors)
```
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>3.2 line segment for 7 temp station, 5 day HW</b>

</h3>

::: {style="display:none;"}
YVR: 1937-2024

Prince_George: 1940-2024

FortNelson: 1937-2024

Kelowna: 1899-2024

Abbotsford: 1935-2024

Kamloops: 1939-2024

Penticton: 1941-2024



#### line segment 5 day

```{r, echo=FALSE,message=FALSE}

df_filtered_line_seg_5d <- df_line_seg_5day[ (df_line_seg_5day$Heatwave) == "Heatwave",]
#df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]

# Check for and remove any remaining NA values in the station column
df_filtered_line_seg_5d <- df_filtered_line_seg_5d %>%
  filter(!is.na(station))
#line_segment_plot(df_filtered_line_seg_5d, station_only = c("YVR", "Prince_George","Kamloops","Kelowna"))+ #geom_hline(aes(yintercept = as.numeric(Year)), color = "grey", linetype = "solid", alpha = 0.5)


df_station_filter<- line_segment_data_prepare(df_filtered_line_seg_5d, station_only = c("YVR", "Prince_George","Kamloops","Kelowna","Abbotsford","Penticton","FortNelson"))
year_ranges <- create_year_ranges(1941, 2024, 5)
hline_data <- generate_temperature_plots("5 days long",df_station_filter, year_ranges, station_colors)

```
:::

<h3 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>3.3 line segment 2 yvr compare, for HW over 3 days </b>

</h3>

<div style="display:none;">

```{r, echo=FALSE,message=FALSE}


station_colors <- c( "YVR" = "blue",
                    'YVR_30y_based' = 'green')

#line_segment_plot(df_line_seg_3day, station_only = c("YVR", "YVR_30y_based"))+ geom_hline(aes(yintercept = #as.numeric(Year)), color = "grey", linetype = "solid", alpha = 0.5)


df_station_yvr_comp <- line_segment_data_prepare(df_line_seg_3day, station_only = c("YVR", "YVR_30y_based"))
year_ranges <- create_year_ranges(1937, 2024, 4)
hline_data <- generate_temperature_plots("3 days long",df_station_yvr_comp, year_ranges, station_colors)
```

<!-- </div> -->

<!-- <h3 onclick="toggleCollapsible(this);"> -->

<!-- <!--TEXT SHOWS: -->

<!-- <b> 3.4 3 temp stations vs YVR_30_year_based, for HW last 3 day</b> -->
<!-- </h3> --> <!-- <div style="display:none;">  -->

<!-- YVR:           1937-2024 -->

<!-- Prince_George: 1942-2024 -->

<!-- Kamloops:      1951-2024 -->

<!-- Kelowna:       1899-2024 -->

<!-- Abbotsford:    1935-2024 -->

<!-- Penticton:     1941-2024 -->

```{r, echo=FALSE,message=FALSE}

# df_filtered_line_seg_3d <- df_line_seg_3day[ (df_line_seg_3day$Heatwave) == "Heatwave",]
# #df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]
# 
# # Define the path to save the CSV file
# save_path <- "../output/3day_hw_week5.csv"
# 
# ## Save the selected columns as a CSV file
# write.csv(df_filtered_line_seg_3d, file = save_path, row.names = FALSE)
# 
# 
# # Check for and remove any remaining NA values in the station column
# df_filtered_line_seg_3d <- df_filtered_line_seg_3d %>%
#   filter(!is.na(station))
# 
# df_station_yvr_comp <- line_segment_data_prepare(df_filtered_line_seg_3d, station_only = c( "Prince_George","Kamloops","Kelowna","Abbotsford","Penticton","YVR_30y_based"))
# year_ranges <- create_year_ranges(1951, 2024, 4)
# hline_data <- generate_temperature_plots(df_station_yvr_comp, year_ranges, station_colors)

```

<!-- </div> -->

<!-- <h1 onclick="toggleCollapsible(this);"> -->

<!-- <!--TEXT SHOWS: -->

<!-- <b>Part 4: Excel table summary for temp diff</b> -->
<!-- </h1> --> <!-- <div style="display:none;">  -->

```{r, echo=FALSE,message=FALSE}
# ## line segment 5 day
# df_filtered_line_seg_5d <- df_line_seg_5day[ (df_line_seg_5day$Heatwave) == "Heatwave",]
# #df_filtered_line_seg <- df_line_seg[!is.na(df_line$daily_max_temp),]
# 
# # Check for and remove any remaining NA values in the station column
# df_filtered_line_seg_5d <- df_filtered_line_seg_5d %>%
#   filter(!is.na(station))
# line_segment_plot(df_filtered_line_seg_5d, station_only = c("YVR_era5", "Prince_George","Kamloops"))

library(readxl)

# Read the Excel file
file_path <- "../data/excel_stations.xlsx"
sheets <- excel_sheets(file_path)

# Function to create plots for each station
create_plots <- function(sheet_name, temp_diff_threshold) {
  # Read the data for the specific sheet
  df <- read_excel(file_path, sheet = sheet_name)
  # Ensure DayOfYear is numeric
  # df <- df %>%
  #   mutate(DayOfYear = as.numeric(gsub("[^0-9]", "", DayOfYear)))
  df <- df %>%
    mutate(Month = sub(".*-(.*)", "\\1", DayOfYear))
  
  # Filter data based on temp_diff threshold
  station_data <- df %>%
    filter(temp_diff > temp_diff_threshold)
  
  if (nrow(station_data) > 0) {
    # Plot distribution of Year
    p1 <- ggplot(station_data, aes(x = Year)) +
      geom_histogram(binwidth = 1, fill = "blue", color = "black") +
      ggtitle(paste("Year Distribution for Station", sheet_name)) +
      xlab("Year") +
      ylab("Frequency")
    print(p1)
    # Save the plot
    #ggsave(paste0("year_distribution_station_", sheet_name, ".png"), plot = p1)
    
    # Extract month from DayOfYear
    # station_data <- station_data %>%
    #   mutate(Month = ceiling(DayOfYear / 30))
    
    # Plot distribution of Year and Month
    # Plot distribution of Year and Month
    p2 <- ggplot(station_data, aes(x = Year, fill = Month)) +
      geom_histogram(binwidth = 1, color = "black", position = "stack") +
      scale_fill_brewer(palette = "Set3") +
      ggtitle(paste("Year and Month Distribution for Station", sheet_name)) +
      xlab("Year") +
      ylab("Frequency")
    print(p2)
    # Save the plot
    #ggsave(paste0("year_month_distribution_station_", sheet_name, ".png"), plot = p2)
  }
}

# Set the temperature difference threshold
temp_diff_threshold <- 5

# Create plots for each sheet
for (sheet in sheets) {
  #create_plots(sheet, temp_diff_threshold)
}

```

</div>
<h1 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Part 4 Monthly maxEHF compare</b>

</h1>
<div style="display:none;">  

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>MAY</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE,fig.width=15, fig.height=8}
# Example usage for July (Month = 7)
ts_plot <- plot_ehf_and_correlation(df_ehf_all, month = 5)
ts_plot
```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>JUN</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE,fig.width=15, fig.height=8}
# Example usage for July (Month = 7)
ts_plot <- plot_ehf_and_correlation(df_ehf_all, month = 6)
ts_plot
```


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>JULY</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE,fig.width=15, fig.height=8}
# Example usage for July (Month = 7)
ts_plot <- plot_ehf_and_correlation(df_ehf_all, month = 7)
ts_plot
```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>AUG</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE,fig.width=15, fig.height=8}
# Example usage for July (Month = 7)
ts_plot <- plot_ehf_and_correlation(df_ehf_all, month = 8)
ts_plot
```