---
title: "Kelowna heat wave analysis"
output: html_document
author: "alex lin "
date: "`r format(Sys.Date(), '%B %d, %Y')`"
---
<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


file_paths <- c("../data/kelow/kelow_1899-1962_p2.csv",
                "../data/kelow/kelow_1899-1962_p3.csv",
                "../data/kelow/kelow_1899-1962.csv",
                "../data/kelow/kelow_1961_1969.csv",
                "../data/kelow/kelow_1968-2005_p2.csv",
                "../data/kelow/kelow_1968-2005.csv",
                "../data/kelow/kelow_2005-2010.csv",
                "../data/kelow/kelow_2009-2024.csv")
station_name <- "Kelowna"
source("../R/read_data.R")  ## read data
results <- process_and_save_data(file_paths, station_name)
df <- results[[1]] 
# Example usage
#df <- update_precipitation(df,"../data/kelow/kelowna_extra_ubco.csv")
# Define the save path
#save_path <- paste0("../output/", station_name, "_raw_filtered_columns.csv")
#write.csv(df, file = save_path, row.names = FALSE)  

source("../R/data_wrangling.R") ## data wrangling
source("../R/data_for_temp_plot.R") ## Modify the data by normalizing dates for plotting, get the data ready, and a function to plot a given year vs baseline
source("../R/data_for_hw_plot.R")  
source("../R/hw_plot_all_year_temp.R") ## all year in grey, baseline blue
source("../R/hw_plot_overview.R") 
source("../R/heatmap_real.R") 
start_year <- 1899
end_year <- 2024

step <- 40


```

```{r, echo=FALSE}
dfff <- df
kelowna_extra <- read.csv("../data/kelow/kelowna_extra_ubco.csv")
#select columns
kelowna_extra <- kelowna_extra %>% select(LOCAL_DATE,TOTAL_PRECIPITATION)

#count na
sum(is.na(dfff$TOTAL_PRECIPITATION))
sum(is.na(kelowna_extra$TOTAL_PRECIPITATION))

# Convert LOCAL_DATE to Date type if it's not already
kelowna_extra$LOCAL_DATE <- as.Date(kelowna_extra$LOCAL_DATE)
dfff$LOCAL_DATE <- as.Date(dfff$LOCAL_DATE)

# Update dfff with values from kelowna_extra where dfff has NA in TOTAL_PRECIPITATION
dfff <- dfff %>%
  left_join(kelowna_extra, by = "LOCAL_DATE", suffix = c("", ".extra")) %>%
  mutate(TOTAL_PRECIPITATION = ifelse(is.na(TOTAL_PRECIPITATION), TOTAL_PRECIPITATION.extra, TOTAL_PRECIPITATION)) %>%
  select(-TOTAL_PRECIPITATION.extra)
sum(is.na(dfff$TOTAL_PRECIPITATION))


```


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>basic EDA</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
# Display the first few rows of the combined data
#print(head(df))

# Display unique station names
unique_stations <- df %>%
  distinct(STATION_NAME)
#print(unique_stations)

# 1. Summary Statistics
summary_stats <- summary(df)
#print(summary_stats)

# 2. Missing Values Analysis
missing_values <- sapply(df, function(x) sum(is.na(x)))
#print(missing_values)
```
</div>

```{r, echo=FALSE,results = 'hide'}
#### check wrangling data
# Print a specific row's rolling window
# df_wrangling$rolling_window[[1]] # First row
# df_wrangling$rolling_window[[5]]  # sample row
# df_wrangling$rolling_window[[10]] # sample row
# df_wrangling$rolling_window[[nrow(df_wrangling)]] # Last row
#get current path

```

```{r, echo=FALSE,results = 'show'}
#check temp dist for in a random day from all year value
# Check the result
#df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[1]] # First row
#df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[5]]  # sample row
# df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[88]] # sample row
# #df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[nrow(df_wrangling)]] # Last row
# length(df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[88]])
unique_stations
```




```{r, echo=FALSE,results = 'show'}
# Print the result
#df_percentiles$Percentile_90

station_name <- "Kelowna"
df_percentiles <- df_percentiles %>%
  mutate(Station = station_name)

# Select specific columns to save
selected_columns <- df_percentiles %>%
  select(Month,Day,Percentile_90,Percentile_95,Station)  # Adjust column names as needed
# Define the path to save the CSV file
save_path <- "../output/Kelowna_percentiles.csv"

## Save the selected columns as a CSV file
write.csv(selected_columns, file = save_path, row.names = FALSE)
```


<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> Plot</b>
</h1>
<div style="display:none;"> 


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> EHF plot</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE}
# filter the date to be April to Aug before slice
df_ehf_top_6 <- df_combined_ehf1 %>%
   filter(month(LOCAL_DATE) >= 4 & month(LOCAL_DATE) <= 8) %>%
  arrange(desc(EHF)) %>%
  slice_head(n = 30)
#unique year
unique(df_ehf_top_6$LOCAL_YEAR)


plot_ehf(df_combined_ehf1,1941)
plot_ehf(df_combined_ehf1,2021)
plot_ehf(df_combined_ehf1,1993)
plot_ehf(df_combined_ehf1,2006)
# Example usage
plot_ehf_all(df_combined_ehf1, start_year, end_year, 1941,station_name)
plot_ehf_all(df_combined_ehf1, start_year, end_year, 2021,station_name)
plot_ehf_all(df_combined_ehf1, start_year, end_year, 1993,station_name)
plot_ehf_all(df_combined_ehf1, start_year, end_year, 2006,station_name)
save_path <- paste0("../output/",station_name,"_monthly_max_EHF.csv")
write.csv(monthly_max_EHF, file = save_path, row.names = FALSE)
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>shows the year with extreme yield </b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}


top_yields
ehf_extreme_yield <- df_combined_ehf1 %>%
  left_join(top_yields, by = c("LOCAL_YEAR" = "REF_DATE")) %>%
  filter(!is.na(Rank)) %>%
  #rename LOCAL_YEAR to Year
  rename(Year = LOCAL_YEAR) %>%
  mutate(DayOfYear = as.integer(format(LOCAL_DATE, "%j")))

#plot_ehf_extreme_yield(ehf_extreme_yield, start_year, end_year, 1990,station_name) 

rank_colors <- c("1" = "red", "2" = "orange", "3" = "yellow", "4" = "green", "5" = "blue")
# base_colors <- c('#FF0000', '#008000', '#0000FF', '#000000', '#FF00FF', '#FFA500', '#FFD700', '#D2691E',
#                  '#D2B48C', '#808000', '#FFFF00', '#40E0D0', '#00BFFF', '#1E90FF', '#8A2BE2', '#FF1493',
#                  '#A52A2A', '#7FFF00', '#8B008B', '#FF69B4','#A9A9A9', '#696969') 

plot_ehf_extreme_yield <- function(ehf_extreme_yield, start_year, end_year, station_name,ranking, top_n = NULL, lowest_n = NULL) {
  # Create an empty data frame to store all years' data
  all_years_data <- ehf_extreme_yield 
  # Loop through each year and bind the data
  # for (year in start_year:end_year) {
  #   df_plot_year <- ehf_extreme_yield %>%
  #     filter(LOCAL_YEAR == year) %>%
  #     mutate(DayOfYear = as.integer(format(LOCAL_DATE, "%j")),
  #            Year = year)
  #   all_years_data <- bind_rows(all_years_data, df_plot_year)
  # }

  # Filter data based on top_n or lowest_n if specified
  if (!is.null(top_n)) {
  all_years_data <- all_years_data %>%
    filter(Type == "Highest") %>%
    filter(Rank %in% ranking)
   title_rank <- paste("Top", top_n, "Highest")
} else if (!is.null(lowest_n)) {
  all_years_data <- all_years_data %>%
    filter(Type == "Lowest") %>%
    filter(Rank %in% ranking)
  title_rank <- paste("Top", lowest_n, "Lowest")
}
  
  all_years_data$Rank <- as.factor(all_years_data$Rank)

  ggplot(all_years_data, aes(x = DayOfYear)) +
    geom_line(aes(y = EHF, color = Rank,group = Year), size = 1, alpha = 0.7) +
    # geom_line(data = filter(all_years_data, Year == specific_year), 
    #           aes(y = EHF), 
    #           color = "red", size = 1.5) +
   scale_color_manual(values = rank_colors, name = "Rank") +
    labs(
      title = paste("EHF Over the Years with", "at", station_name), #title_rank,
      x = "Day of Year",
      y = "EHF"
    ) +
    theme_minimal(base_size = 11) +
    theme(plot.margin = margin(20, 20, 20, 20)) +
    theme(aspect.ratio = 1/2) +
    # scale_x_continuous(
    #   breaks = seq(1, 365, by = 5),
    #   labels = function(x) format(as.Date(x, origin = "1970-01-01"), "%b %d")
    # ) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 6),
          plot.title = element_text(size = 14, face = "bold"),
          axis.title = element_text(size = 12))
  # Plot all years with color based on Rank intensity and highlight the specific year
  
}
plot_ehf_extreme_yield(ehf_extreme_yield,start_year, end_year, "Kelowna",  (1:5),  top_n = 2)



top_yields
data_pot
ehf_potato <- df_combined_ehf1 %>%
  filter(month(LOCAL_DATE) >= 3 & month(LOCAL_DATE) <= 10) %>%
  filter(LOCAL_YEAR >= 1910 & LOCAL_YEAR <= 2024)


plot_ehf_all(ehf_potato, start_year, end_year, 1995,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield:", data_pot %>% filter(REF_DATE == 1995) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1989,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1989) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1915,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1915) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1992,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1992) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1979,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1979) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_extreme_yield(ehf_extreme_yield,start_year, end_year, "Kelowna",  (1:5),  lowest_n   = 2)

plot_ehf_all(ehf_potato, start_year, end_year, 1990,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1990) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1981,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1981) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1993,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1993) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1997,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1997) %>% pull(Detrended_Yield_LOESS)), color = "red", size = 5, hjust = 0, vjust = 0)
plot_ehf_all(ehf_potato, start_year, end_year, 1951,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1951) %>% pull(Detrended_Yield)), color = "red", size = 5, hjust = 0, vjust = 0)

```
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}

plot_ehf_all(ehf_potato, start_year, end_year, 2021,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 2021) %>% pull(Detrended_Yield)), color = "red", size = 5, hjust = 0, vjust = 0)

plot_ehf_all(ehf_potato, start_year, end_year, 1941,station_name) + annotate("text", x = 200, y = 100, label =paste( "Detrended_Yield_LOESS:", data_pot %>% filter(REF_DATE == 1941) %>% pull(Detrended_Yield)), color = "red", size = 5, hjust = 0, vjust = 0)
```

```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Assuming `ehf_extreme_yield` has columns 'Day_of_Year', 'EHF', and 'Rank'
ehf_extreme_yield <- ehf_extreme_yield %>%
  mutate(Rank_Group = case_when(
    Rank <= 3 ~ "1-3 Highest",
    Rank <= 6 ~ "4-6 Highest",
    TRUE ~ "1-3 Lowest"
  ))
library(ggplot2)

ggplot(ehf_extreme_yield, aes(x = LOCAL_DATE, y = EHF, color = Rank_Group)) +
  geom_line() +
   +
  labs(title = "EHF Over the Years with Rank Indications",
       x = "Day of Year", y = "EHF",
       color = "Rank Group") +
  theme_minimal()


```
</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot 90th compare different based year  </b>
</h3>
<div style="display:none;"> 
```{r, echo=FALSE,message=FALSE, warning=FALSE}
compare_plot
compare_plot_95
```

</div>

<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot certain year temp dist vs baseline 90th </b>
</h3>
<div style="display:none;"> 



```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.path="Kelowna_heatwave_analysis_files/",fig.cap="Plot caption",fig.show='hold'}
df_plot_year_begin <- prepare_plot_data("Percentile_90", 1941, "MAX_TEMPERATURE")

plot_percentiles_vs_year(df_plot_year_begin,1941)
#

```

```{r, echo=FALSE, warning=FALSE}

# Example usage:
df_plot_year <- prepare_plot_data("Percentile_90", 2021, "MAX_TEMPERATURE")
# Example usage:

plot_percentiles_vs_year(df_plot_year,2021)
```

</div>

<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot  90th (blue) vs all year temp dist (grey). Based line is all year.</b>
</h3>
<div style="display:none;"> 

```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Main function to loop through multiple years
plot_all_years <- function(start_year, end_year) {
  for (year in start_year:end_year) {
    df_plot_year <- prepare_plot_data("Percentile_90", year, "MAX_TEMPERATURE")
    print(plot_percentiles_vs_year(df_plot_year, year))
  }
}
#plot_all_years(2000, 2024)

```




```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Example usage:
#Assuming the range of years is from 2000 to 2024 and the specific year to highlight is 2014

#print(plot_all_years_with_baseline(start_year,end_year,2000))


#print(plot_all_years_highlight_specific_year(start_year,end_year,1941))
print(plot_all_years_highlight_specific_year(1941,1950,1941))
```

```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Example usage:
#print(plot_all_years_highlight_specific_year(start_year,end_year,1940))

```   

</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Analyze the hw </b>
</h1>
<div style="display:none;">  



</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>prepare for the data </b>
</h4>
<div style="display:none;">  

```{r, echo=FALSE,message=FALSE, warning=FALSE}
year_analysis_hw <- 2019
df_for_hw <- prepare_plot_data("Percentile_90", year_analysis_hw, "MAX_TEMPERATURE")
process_data_for_hw(df_for_hw)

```




```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Analysis for each year
# Define the start, end, and step for the sequence


# Generate the sequence of years
years <- seq(start_year, end_year, by = step)

# Loop over the sequence of years
for (year_single in years) {
  #df_plot <- prepare_plot_data("Percentile_90", year_single, "MAX_TEMPERATURE")
  #summaries <- process_data_by_year(process_data_for_hw(df_plot), year_single)
  #plots <- plot_case_summary(summaries, year_single)
  
  #print(plots$month_plot)
  #print(plots$hw_length_plot)
}

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>plot overall count of hw through years </b>
</h3>
<div style="display:none;"> 

```{r, echo=FALSE,message=FALSE}
# Process all years and generate plots

summary_df_hw_day <- process_all_years_and_generate_plots(start_year,1980)

# Print the generated plots
#print(plots$total_plot)
#summary_df_hw_day

```

```{r, echo=FALSE,,message=FALSE}
# Process all years and generate plots

summary_df_hw_day <- process_all_years_and_generate_plots(1980,end_year)
# Print the generated plots
#summary_df_hw_day
```


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>plot for heat map</b>
</h3>
<div style="display:none;">  

```{r, echo=FALSE,message=FALSE}
# Assuming you have data frames named df_2021, df_2022, ..., df_2025
# Loop through the years to dynamically add each data frame to the list
 list_of_dfs <- list()
 
 for (year in start_year:end_year) {
   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
   
   # Add the prepared data frame to the list
   list_of_dfs[[as.character(year)]] <- prepared_df
 }
 # Combine the data frames into one
 combined_df <- do.call(rbind, list_of_dfs)
 
```



```{r, echo=FALSE,message=FALSE}
#combined_df

selected_columns <- combined_df %>%
  select(Year,DayOfYear,Max_Temp_Year,Percentile_90,Station)  # Adjust column names as needed
# Define the path to save the CSV file
save_path <- "../output/Kelowna_heatmap_data.csv"

## Save the selected columns as a CSV file
write.csv(selected_columns, file = save_path, row.names = FALSE)

```

```{r, echo=FALSE,message=FALSE}

heatmap <- create_heatmap(combined_df, "01-01","12-31")
print(heatmap)
 
```


```{r, echo=FALSE,message=FALSE}

heatmap <- create_heatmap(combined_df, "04-01","10-31")
print(heatmap)
 
```



```{r, echo=FALSE,message=FALSE}

result_df_3_Kelowna <- create_heatmap_filter_hw(combined_df, heat_wave_length = 3, start_date = '04-01', end_date = '10-31') 
df_3_Kelowna <- result_df_3_Kelowna[[1]]
df_3_Kelowna_95 <- result_df_3_Kelowna[[2]]

result_df_5_Kelowna <-  create_heatmap_filter_hw(combined_df, heat_wave_length = 5, start_date = '04-01', end_date = '10-31') 
df_5_Kelowna <- result_df_5_Kelowna[[1]]
df_5_Kelowna_95 <- result_df_5_Kelowna[[2]]
```



```{r, echo=FALSE,message=FALSE}


#df_3_Kelowna
# Rename the column
colnames(df_3_Kelowna)[colnames(df_3_Kelowna) == "Color"] <- "daily_max_temp"
# Add the new column
df_3_Kelowna$station <- "Kelowna"
# Save the updated dataframe to a file
write.csv(df_3_Kelowna, "../output/Kelowna_heatmap_3_dayHW.csv", row.names = FALSE)


#df_5_Kelowna
# Rename the column
colnames(df_5_Kelowna)[colnames(df_5_Kelowna) == "Color"] <- "daily_max_temp"
# Add the new column
df_5_Kelowna$station <- "Kelowna"
# Save the updated dataframe to a file

write.csv(df_5_Kelowna, "../output/Kelowna_heatmap_5_dayHW.csv", row.names = FALSE)



colnames(df_3_Kelowna_95)[colnames(df_3_Kelowna_95) == "Color_95"] <- "daily_max_temp"
# Add the new column
df_3_Kelowna_95$station <- "Kelowna"
# Save the updated dataframe to a file
write.csv(df_3_Kelowna_95, "../output/Kelowna_heatmap_3_dayHW_95.csv", row.names = FALSE)


#df_5_Kelowna
# Rename the column
colnames(df_5_Kelowna_95)[colnames(df_5_Kelowna_95) == "Color_95"] <- "daily_max_temp"
# Add the new column
df_5_Kelowna_95$station <- "Kelowna"
# Save the updated dataframe to a file
write.csv(df_5_Kelowna_95, "../output/Kelowna_heatmap_5_dayHW_95.csv", row.names = FALSE)

```




```{r, echo=FALSE,message=FALSE}

heatmap <- create_heatmap_diff(combined_df, "04-01","10-31")
print(heatmap)
 
```

```{r, echo=FALSE,message=FALSE}

df_3_Kelowna <- create_heatmap_diff_filter_hw(combined_df, heat_wave_length = 3, start_date = '04-01', end_date = '10-31') 

df_5_Kelowna <-create_heatmap_diff_filter_hw(combined_df, heat_wave_length = 5, start_date = '04-01', end_date = '10-31') 

```

## seperate view of the heatmap
```{r, echo=FALSE,message=FALSE}
# list_of_dfs <- list()
# 
# for (year in 1941:1960) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# 
# list_of_dfs <- list()
# for (year in 1960:1980) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# list_of_dfs <- list()
# for (year in 1980:2000) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)


# 
# list_of_dfs <- list()
# for (year in 2000:2024) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
 
```


## examine specific year (grep line vs 90 vs specific year)
```{r, echo=FALSE,message=FALSE}
# Define the specific years you want to process
# years_to_process <- c(1947,1958,1970, 2009, 2021)
# 
# # Initialize an empty list to store data frames for each year
# list_of_dfs <- list()
#   
# for (year in years_to_process) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# for (year in years_to_process) {
#   print(plot_all_years_highlight_specific_year(start_year,end_year,year))
# }
```
## according bar
```{r, echo=FALSE,message=FALSE}
# # Loop over the sequence of years
# years_to_process <- c(1947,1958,1970, 2009, 2021)
# for (year_single in years_to_process) {
#   df_plot <- prepare_plot_data("Percentile_90", year_single, "MAX_TEMPERATURE")
#   summaries <- process_data_by_year(process_data_for_hw(df_plot), year_single)
#   plots <- plot_case_summary(summaries, year_single)
#   
#   print(plots$month_plot)
#   print(plots$hw_length_plot)
#}
```


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> Plot EHF vs Percentile_90 for specific year</b>
</h3>
<div style="display:none;">  

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>1958</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}



results_2def <- full_compare_ehf_and_percentile_specific(df_combined_ehf1, 1958)
combined_plot_2021 <- results_2def[[1]]
left_full <- results_2def[[2]] 
left_full
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>1971</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}



results_2def <- full_compare_ehf_and_percentile_specific(df_combined_ehf1, 1971)
combined_plot_2021 <- results_2def[[1]]
left_full <- results_2def[[2]] 
left_full
```


</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>1998</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}



results_2def <- full_compare_ehf_and_percentile_specific(df_combined_ehf1, 1998)
combined_plot_2021 <- results_2def[[1]]
left_full <- results_2def[[2]] 
left_full
```


</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>2021</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}



results_2def <- full_compare_ehf_and_percentile_specific(df_combined_ehf1, 2021)
combined_plot_2021 <- results_2def[[1]]
left_full <- results_2def[[2]] 
left_full
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>2022</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,message=FALSE, warning=FALSE,fig.width=10}



results_2def <- full_compare_ehf_and_percentile_specific(df_combined_ehf1, 2022)
combined_plot_2021 <- results_2def[[1]]
left_full <- results_2def[[2]] 
left_full
```