---
title: "week3 PRINCE GEORGE heat wave analysis"
output: html_document
date: "2024-05-20"
---
<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>
# Data {.collapsible}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
file_paths <- c("../data/Prince_George 1942 Climate data daily.csv",
                "../data/Prince_George Climate data daily (1).csv",
                "../data/Prince_Geo_2009_to_2024.csv",
                "../data/Prince_Geo_1997_to_2009.csv",
                "../data/Prince_George_1940-1942.csv")
station_name <- "Prince_George" 
source("../R/read_data.R")  ## read data
df <- process_and_save_data(file_paths, station_name)
source("../R/data_wrangling.R") ## data wrangling
source("../R/data_for_temp_plot.R") ## Modify the data by normalizing dates for plotting, get the data ready, and a function to plot a given year vs baseline
source("../R/data_for_hw_plot.R")  
source("../R/hw_plot_all_year_temp.R") ## all year in grey, baseline blue
source("../R/hw_plot_overview.R") 
source("../R/heatmap_real.R") 
start_year <- 1940
end_year <- 2024
step <- 40
```



<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>basic EDA</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
# Display the first few rows of the combined data
#print(head(df))

# Display unique station names
unique_stations <- df %>%
  distinct(STATION_NAME)
#print(unique_stations)

# 1. Summary Statistics
summary_stats <- summary(df)
#print(summary_stats)

# 2. Missing Values Analysis
missing_values <- sapply(df, function(x) sum(is.na(x)))
#print(missing_values)
```
</div>
```{r, echo=FALSE,results = 'hide'}
# Print a specific row's rolling window
# df_wrangling$rolling_window[[1]] # First row
# df_wrangling$rolling_window[[5]]  # sample row
# df_wrangling$rolling_window[[10]] # sample row
# df_wrangling$rolling_window[[nrow(df_wrangling)]] # Last row
```
check temp dist for in a random day from all year value
```{r, echo=FALSE,results = 'show'}
# Check the result
#df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[1]] # First row
#df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[5]]  # sample row
#df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[88]] # sample row
#df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[nrow(df_wrangling)]] # Last row
#length(df_grouped$ROLLING_WINDOW_ALL_YEAR_VALUES[[88]])
unique_stations
```


get 90th from the all year for all day value
```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Print the result
#df_percentiles$Percentile_90
station_name <- "Prince_George"
df_percentiles <- df_percentiles %>%
  mutate(Station = station_name)

# Select specific columns to save
selected_columns <- df_percentiles %>%
  select(Month,Day,Percentile_90,Station)  # Adjust column names as needed
# Define the path to save the CSV file
save_path <- "../output/PriGeog_percentiles.csv"

## Save the selected columns as a CSV file
write.csv(selected_columns, file = save_path, row.names = FALSE)
```

# Plot

## plot given year temp dist vs baseline 90th

```{r, echo=FALSE,message=FALSE, warning=FALSE}
compare_plot
# Example usage:
df_plot_year <- prepare_plot_data("Percentile_90", 1941, "MAX_TEMPERATURE")
# Example usage:
plot_percentiles_vs_year(df_plot_year,1941)
```
```{r, echo=FALSE,message=FALSE, warning=FALSE}

# Example usage:
df_plot_year <- prepare_plot_data("Percentile_90", 2021, "MAX_TEMPERATURE")
# Example usage:
plot_percentiles_vs_year(df_plot_year,2021)
```


```{r, echo=FALSE,message=FALSE, warning=FALSE}
# Main function to loop through multiple years
plot_all_years <- function(start_year, end_year) {
  for (year in start_year:end_year) {
    df_plot_year <- prepare_plot_data("Percentile_90", year, "MAX_TEMPERATURE")
    print(plot_percentiles_vs_year(df_plot_year, year))
  }
}
#plot_all_years(2000, 2024)

```



## plot all year temp in grey vs baseline 
```{r, echo=FALSE,message=FALSE}
# Example usage:
#Assuming the range of years is from 2000 to 2024 and the specific year to highlight is 2014

#print(plot_all_years_with_baseline(start_year,end_year,2000))

print(plot_all_years_highlight_specific_year(start_year,end_year,1941))
print(plot_all_years_highlight_specific_year(start_year,end_year,2021))
```


```{r, echo=FALSE,message=FALSE}
# Example usage:
#Assuming the range of years is from 2000 to 2024 and the specific year to highlight is 2014
#print(plot_all_years_highlight_specific_year(start_year,end_year,2020))
#print(plot_all_years_highlight_specific_year(start_year,end_year,2022))
#print(plot_all_years_highlight_specific_year(start_year,end_year,2019))
```

## Analyze the hw

## hw dist for certain 1 year

prepare for the data
```{r, echo=FALSE,message=FALSE}
year_analysis_hw <- 2019
df_for_hw <- prepare_plot_data("Percentile_90", year_analysis_hw, "MAX_TEMPERATURE")
process_data_for_hw(df_for_hw)
```


## plot hw analysis for all year

```{r, echo=FALSE,message=FALSE}
# Analysis for each year
# Define the start, end, and step for the sequence


# Generate the sequence of years
years <- seq(start_year, end_year, by = step)

# Loop over the sequence of years
for (year_single in years) {
  # df_plot <- prepare_plot_data("Percentile_90", year_single, "MAX_TEMPERATURE")
  # summaries <- process_data_by_year(process_data_for_hw(df_plot), year_single)
  # plots <- plot_case_summary(summaries, year_single)
  # 
  # print(plots$month_plot)
  # print(plots$hw_length_plot)
}

```

## plot overall count of hw through years

```{r, echo=FALSE,message=FALSE}
# Process all years and generate plots
summary_df_hw_day <- process_all_years_and_generate_plots(start_year,1980)

# Print the generated plots
#print(plots$total_plot)
#print(summary_df_hw_day)

```

```{r, echo=FALSE,,message=FALSE}
# Process all years and generate plots
summary_df_hw_day <- process_all_years_and_generate_plots(1980,end_year)

# Print the generated plots
#print(summary_df_hw_day)
```

## plot for heat map


```{r, echo=FALSE,message=FALSE}
# Assuming you have data frames named df_2021, df_2022, ..., df_2025
# Loop through the years to dynamically add each data frame to the list
 list_of_dfs <- list()
 
 for (year in start_year:end_year) {
   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
   
   # Add the prepared data frame to the list
   list_of_dfs[[as.character(year)]] <- prepared_df
 }
 # Combine the data frames into one
 combined_df <- do.call(rbind, list_of_dfs)
```


```{r, echo=FALSE,message=FALSE}
#combined_df

selected_columns <- combined_df %>%
  select(Year,DayOfYear,Max_Temp_Year,Percentile_90,Station)  # Adjust column names as needed
# Define the path to save the CSV file
save_path <- "../output/Prince_George_heatmap_data.csv"

## Save the selected columns as a CSV file
write.csv(selected_columns, file = save_path, row.names = FALSE)

```


```{r, echo=FALSE,message=FALSE}
heatmap <- create_heatmap(combined_df, "01-01","12-31")
print(heatmap)
```


```{r, echo=FALSE,message=FALSE}
heatmap <- create_heatmap(combined_df, "04-01","10-31")
print(heatmap)
 
```



```{r, echo=FALSE,message=FALSE}
df_3_yvr <- create_heatmap_filter_hw(combined_df, heat_wave_length = 3, start_date = '04-01', end_date = '10-31') 
df_5_yvr <-  create_heatmap_filter_hw(combined_df, heat_wave_length = 5, start_date = '04-01', end_date = '10-31') 

```


```{r, echo=FALSE,message=FALSE}
#df_3_yvr
# Rename the column
colnames(df_3_yvr)[colnames(df_3_yvr) == "Color"] <- "daily_max_temp"
# Add the new column
df_3_yvr$station <- "Prince_George"
# Save the updated dataframe to a file
write.csv(df_3_yvr, "../output/Prince_George_heatmap_3_dayHW.csv", row.names = FALSE)


#df_5_yvr
# Rename the column
colnames(df_5_yvr)[colnames(df_5_yvr) == "Color"] <- "daily_max_temp"
# Add the new column
df_5_yvr$station <- "Prince_George"
# Save the updated dataframe to a file
write.csv(df_5_yvr, "../output/Prince_George_heatmap_5_dayHW.csv", row.names = FALSE)

```



```{r, echo=FALSE,message=FALSE}
heatmap <- create_heatmap_diff(combined_df, "04-01","10-31")
print(heatmap)
```


```{r, echo=FALSE,message=FALSE}
df_3_yvr <- create_heatmap_diff_filter_hw(combined_df, heat_wave_length = 3, start_date = '04-01', end_date = '10-31') 
df_5_yvr <-create_heatmap_diff_filter_hw(combined_df, heat_wave_length = 5, start_date = '04-01', end_date = '10-31') 

```

## seperate view of the heatmap
```{r, echo=FALSE,message=FALSE}
# list_of_dfs <- list()
# 
# for (year in 1941:1960) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# 
# list_of_dfs <- list()
# for (year in 1960:1980) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# list_of_dfs <- list()
# for (year in 1980:2000) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# 
# 
# list_of_dfs <- list()
# for (year in 2000:2024) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
 
```





## examine specific year
```{r, echo=FALSE,message=FALSE}
# # Define the specific years you want to process
# #years_to_process <- c(1944,1950,1958,1969,1977,1983, 2005,2021)
# years_to_process <- c(2021)
# # Initialize an empty list to store data frames for each year
# list_of_dfs <- list()
#   
# for (year in years_to_process) {
#   # Assuming `df` is the base data frame, apply the `prepare_heatmap_plot_data` function
#   prepared_df <- prepare_heatmap_plot_data(df, "Percentile_90", year, "MAX_TEMPERATURE")
#   
#   # Add the prepared data frame to the list
#   list_of_dfs[[as.character(year)]] <- prepared_df
# }
# # Combine the data frames into one
# combined_df2 <- do.call(rbind, list_of_dfs)
# 
# heatmap <- create_heatmap_diff(combined_df2, "04-01","10-31")
# print(heatmap)
# 
# for (year in years_to_process) {
#   print(plot_all_years_highlight_specific_year(start_year,end_year,year))
# }
```

```{r, echo=FALSE,message=FALSE}
#for (year in 2013:2015) {
#  print(plot_all_years_highlight_specific_year(start_year,end_year,year))
#}
```

```{r, echo=FALSE,message=FALSE}
# # Loop over the sequence of years
# years_to_process <- c(1944,1950,1958,1969,1977,1983, 2005,2021)
# for (year_single in years_to_process) {
#   df_plot <- prepare_plot_data("Percentile_90", year_single, "MAX_TEMPERATURE")
#   summaries <- process_data_by_year(process_data_for_hw(df_plot), year_single)
#   plots <- plot_case_summary(summaries, year_single)
#   
#   print(plots$month_plot)
#   print(plots$hw_length_plot)
# }
```
