---
title: "agricluture linear regression model"
author: "alex lin "
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---


<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>



```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R_agricultural/explore_qualified_crop.R")  ## explore qualified crop
source("../R_agricultural/read_data.R")  ## read data
source("../R_agricultural/data_wrangling.R")  ## data wrangling
source("../R_agricultural/model_potato.R")  ## plot yield over time
source("../R_agricultural/ranking_yield.R")  ## plot yield over time

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# FILTER data_x to start from 1961 as it is the start of the FAO data
#LOCAL_DATE
data_x <- data_x %>%
  filter(LOCAL_DATE >= "1961-01-01")

weekly_data_x <- aggregate_data_week(data_x)
monthly_data_x <- aggregate_data_month(data_x,agg_method = "max")
season_data_x <- aggregate_data_season(data_x,agg_method = "max")
```

<h1 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Part 1: veg data</b>

</h1>


```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

veg_year
veg_year_2
# Use the functions
long_data <- process_data(data_veg_1940,"green peas")

# Define custom colors
custom_colors <- c(
  "Average_yield_per_acre_pounds" = "red",
  "Average_yield_per_hectare_kilograms" = "blue",
  "yield_tp_ah_acre_pounds" = "#008000",
  "yield_tp_ah_hectare_kg" = "#FF00FF",
  "yield_mp_ap_acre_pounds" = "#FFFF00",
  "yield_mp_ap_hectare_kg" = "#A52A2A",
  "yield_mp_ah_acre_pounds" = "#696969",
  "yield_mp_ah_hectare_kg" = "#40E0D0",
  "yield_tp_ap_acre_pounds" = "#FF1493",
  "yield_tp_ap_hectare_kg" = "#1E90FF"
)
# Plot all yields
plot_yields(long_data, custom_colors)

# Plot selected yields
selected_yield_types <- c("Average_yield_per_acre_pounds", "yield_mp_ah_hectare_kg", "yield_tp_ap_acre_pounds","yield_mp_ah_acre_pounds","yield_tp_ap_hectare_kg")
plot_selected_yields(long_data, selected_yield_types, custom_colors)




```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

# data_veg_1940
# 
# veg_year_2
# unique(data_veg_1940$Crop_Type)
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=4}
#plot data_veg_1940 yield for diff type of veg
#each type is a plot

#check the rest crop yield is good

# data_veg_1940_yield <- data_veg_1940 %>%
#   filter(Estimates == "Average yield per acre (pounds)")
# for (i in unique(data_veg_1940_yield$Crop_Type)){
#   p <- ggplot(data_veg_1940_yield %>% filter(Crop_Type == i), aes(x = REF_DATE, y = VALUE)) +
#     geom_line() +
#     geom_point() +
#     labs(title = paste("Yield of Crops over Time for", i),
#          x = "Year",
#          y = "Yield",
#          color = "Crop Type") +
#     theme_minimal() 
#   print(p)
# }

```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>plot **good** quality replacement for yield data </b>

</h4>

::: {style="display:none;"}
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=18, fig.height=7}

# List of crops categorized by quality
good_quality <- list("spinach", "lettuce", "sweet corn")
ok_quality <- list("asparagus", "cabbage")
soso_quality <- list("carrots", "celery", "green peas", "rutabagas and turnips")
mixed_quality <- list("green and wax beans", "parsnips")
bad_quality <- list("beets","cauliflowers", "dry onions")



#for loop
for (c in good_quality){
  complete_data <- handle_missing_yield(data_veg_1940,crop_type = c)##green peas
  filter_data <- data_veg_1940 %>%
    filter(Crop_Type == c)
  backup_yield <- prepare_backup_yield(filter_data)
  merged_yield <- merge(complete_data, backup_yield, by = c("REF_DATE"), all.x = TRUE, suffixes = c("_Production", "_Area"))
  
  p <- plot_yield_over_time(merged_yield)
  #add a vertical line
  p <- p + geom_vline(xintercept = 2021, linetype = "dashed",color = "red")
  print(p)
}




```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>plot **ok** quality replacement for yield data </b>

</h4>

::: {style="display:none;"}
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
for (c in ok_quality){
  complete_data <- handle_missing_yield(data_veg_1940,crop_type = c)##green peas
  filter_data <- data_veg_1940 %>%
    filter(Crop_Type == c)
  backup_yield <- prepare_backup_yield(filter_data)
  merged_yield <- merge(complete_data, backup_yield, by = c("REF_DATE"), all.x = TRUE, suffixes = c("_Production", "_Area"))
  
  p <- plot_yield_over_time(merged_yield)
  #add a vertical line
  p <- p + geom_vline(xintercept = 2021, linetype = "dashed",color = "red")
  print(p)
}




```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>plot **soso** quality replacement for yield data </b>

</h4>

::: {style="display:none;"}
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
for (c in soso_quality){
  complete_data <- handle_missing_yield(data_veg_1940,crop_type = c)##green peas
  filter_data <- data_veg_1940 %>%
    filter(Crop_Type == c)
  backup_yield <- prepare_backup_yield(filter_data)
  merged_yield <- merge(complete_data, backup_yield, by = c("REF_DATE"), all.x = TRUE, suffixes = c("_Production", "_Area"))
  
  p <- plot_yield_over_time(merged_yield)
  #add a vertical line
  p <- p + geom_vline(xintercept = 2021, linetype = "dashed",color = "red")
  print(p)
}
```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>plot **mixed** quality replacement for yield data </b>

</h4>

::: {style="display:none;"}
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
for (c in mixed_quality){
  complete_data <- handle_missing_yield(data_veg_1940,crop_type = c)##green peas
  filter_data <- data_veg_1940 %>%
    filter(Crop_Type == c)
  backup_yield <- prepare_backup_yield(filter_data)
  merged_yield <- merge(complete_data, backup_yield, by = c("REF_DATE"), all.x = TRUE, suffixes = c("_Production", "_Area"))
  
  p <- plot_yield_over_time(merged_yield)
  #add a vertical line
  p <- p + geom_vline(xintercept = 2021, linetype = "dashed",color = "red")
  print(p)
}
```
:::

<h4 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>plot **bad** quality replacement for yield data </b>

</h4>

::: {style="display:none;"}
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
for (c in bad_quality){
  complete_data <- handle_missing_yield(data_veg_1940,crop_type = c)##green peas
  filter_data <- data_veg_1940 %>%
    filter(Crop_Type == c)
  backup_yield <- prepare_backup_yield(filter_data)
  merged_yield <- merge(complete_data, backup_yield, by = c("REF_DATE"), all.x = TRUE, suffixes = c("_Production", "_Area"))
  
  p <- plot_yield_over_time(merged_yield)
  #add a vertical line
  p <- p + geom_vline(xintercept = 2021, linetype = "dashed",color = "red")
  print(p)
}
```
:::

<h1 onclick="toggleCollapsible(this);">

<!--TEXT SHOWS: -->

<b>Part 2: patato data</b>

</h1>

<div style="display:none;">

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
mov_avg
LOESS_avg

```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
#### eg--------------
p <- lm_monthly_potato(monthly_data_x, data_pot, "Kelowna", "maxmon_EHF_95","VALUE")
print(p)

p <- lm_monthly_potato(monthly_data_x, data_pot, "Abbotsford", "maxmon_EHF_95","VALUE")
print(p)


# [1] "REF_DATE" "VALUE"    "Moving_Avg" "Detrended_Yield" 
#"Loess_Trend_LOESS" "Detrended_Yield_LOESS"
#
p <- lm_monthly_potato(monthly_data_x, data_pot, "Kelowna", "maxmon_EHF_95","Detrended_Yield_LOESS")
print(p)

p <- lm_monthly_potato(monthly_data_x, data_pot, "Kelowna", "maxmon_EHF_95","Detrended_Yield")
print(p)


lm_onemonth_potato(monthly_data_x, data_pot, "Kelowna", "maxmon_EHF_95", "VALUE")
lm_onemonth_potato(monthly_data_x, data_pot, "Kelowna", "maxmon_EHF_95", "Detrended_Yield")
lm_onemonth_potato(monthly_data_x, data_pot, "Kelowna", "maxmon_EHF_95", "Detrended_Yield_LOESS")

```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

re <- lm_season_potato(season_data_x, data_pot, 
                       "Kelowna", "maxsea_EHF_95", "VALUE")
re2 <- lm_season_potato(season_data_x, data_pot, 
                       "Kelowna", "maxsea_EHF_95", "Detrended_Yield")
re3 <- lm_season_potato(season_data_x, data_pot,
                       "Kelowna", "maxsea_EHF_95", "Detrended_Yield_LOESS")

print(re)
print(re2)
print(re3)

```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

re <- lm_season_potato(season_data_x, data_pot, 
                       "Kelowna", "maxsea_Mean_Temp", "VALUE")
re2 <- lm_season_potato(season_data_x, data_pot, 
                       "Kelowna", "maxsea_Mean_Temp", "Detrended_Yield")
re3 <- lm_season_potato(season_data_x, data_pot,
                       "Kelowna", "maxsea_Mean_Temp", "Detrended_Yield_LOESS")

print(re)
print(re2)
print(re3)
colnames(season_data_x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
#colnames(data_pot)
# 1] "REF_DATE"              "VALUE"                 "UOM"                  
# [4] "Crop_Type"             "Moving_Avg"            "Detrended_Yield"      
# [7] "Loess_Trend_LOESS"     "Detrended_Yield_LOESS"
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
#colnames(data_pot)
# 1] "REF_DATE"              "VALUE"                 "UOM"                  
# [4] "Crop_Type"             "Moving_Avg"            "Detrended_Yield"      
# [7] "Loess_Trend_LOESS"     "Detrended_Yield_LOESS"
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=10, fig.height=6}
# plot hist for data_pot in Detrended_Yield

ggplot(data_pot, aes(x = Detrended_Yield_LOESS)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  labs(title = "Histogram of Detrended Potato Yields",
       x = "Detrended Potato Yield",
       y = "Frequency") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(-50,40, by = 10))
#min(data_pot$Detrended_Yield_LOESS), max(data_pot$Detrended_Yield_LOESS)

#box plot
ggplot(data_pot, aes(x = REF_DATE, y = Detrended_Yield_LOESS)) +
  geom_boxplot() +
  labs(title = "Boxplot of Detrended Potato Yields",
       x = "Year",
       y = "Detrended Potato Yield") +
  theme_minimal() +
  coord_flip()

```
