---
title: "FAOSTAT"
author: "alex lin "
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---
<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R_agricultural/explore_qualified_crop.R")  ## explore qualified crop
source("../R_agricultural/read_data.R")  ## read data
source("../R_agricultural/data_wrangling.R")  ## data wrangling

```
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Plot</b>
</h1>
<div style="display:none;">  

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>EDA Plot for each crop data</b>
</h3>
<div style="display:none;">  
```{r}

plot_fao_data(data_fao)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
# FILTER data_x to start from 1961 as it is the start of the FAO data
#LOCAL_DATE
data_x <- data_x %>%
  filter(LOCAL_DATE >= "1961-01-01")

weekly_data_x <- aggregate_data_week(data_x)
monthly_data_x <- aggregate_data_month(data_x)

```
</div>

<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>linear reg for yield VS EHF 95</b>
</h3>
<div style="display:none;">  
</div>

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Abbotsford weekly</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_linear_regression_weekly(weekly_data_x, data_fao,"Abbotsford", "week_Mean_EHF_95")

unique_crops <- unique(data_fao$Item)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
}

```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Kelowna weekly</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_linear_regression_weekly(weekly_data_x, data_fao,"Kelowna", "week_Mean_EHF_95")

unique_crops <- unique(data_fao$Item)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
}

```

</div>

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Abbotsford monthly</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_linear_regression_monthly(monthly_data_x, data_fao,"Abbotsford", "maxmon_EHF_95")

unique_crops <- unique(data_fao$Item)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
}

```


</div>

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Kelowna monthly</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_linear_regression_monthly(monthly_data_x, data_fao,"Kelowna", "maxmon_EHF_95")

unique_crops <- unique(data_fao$Item)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
  
  
  
}

```


</div>

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> FortStJohn monthly</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_linear_regression_monthly(monthly_data_x, data_fao,"FortStJoh", "maxmon_EHF_95")

unique_crops <- unique(data_fao$Item)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
  
  
  
}

```


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>linear reg for yield VS weekly Max Temp</b>
</h3>
<div style="display:none;">  
</div>

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Abbotsford</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_linear_regression_weekly(weekly_data_x, data_fao,"Abbotsford", "week_Mean_Temperature")

unique_crops <- unique(data_fao$Item)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
}

```




```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize the data by Crop_Type to get the year range
crop_year<- crop_yield %>%
  group_by(Crop_Type) %>%
  summarize(Start_Year = min(REF_DATE), End_Year = max(REF_DATE))
crop_year

```



</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Part 4: new crop data</b>
</h1>
<div style="display:none;">  


</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>4.1:field crop data</b>
</h2>
<div style="display:none;">  
</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>yield</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
base_colors <- c('#FF0000', '#008000', '#0000FF', '#FF00FF', '#FFD700', 
                  '#8B008B') 

# Summarize production by year and crop type
# Plot the data
ggplot(crop_yield, aes(x = REF_DATE, y = yield, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  #color
  scale_color_manual(values = base_colors) +
  labs(title = "yield of Crops over Time",
       x = "Year",
       y = "Average yield (kilograms per hectare)",
       color = "Crop Type") +
  theme_minimal() +
  facet_wrap(~GEO)
```


</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>total production</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
# Summarize production by year and crop type
# Plot the data
ggplot(total_produ, aes(x = REF_DATE, y = Production, color = Crop_Type)) +
  geom_line() +
  geom_point() +
    scale_color_manual(values = base_colors) +
  labs(title = "Total Production (metric tonnes) over Time",
       x = "Year",
       y = "Total Production",
       color = "Crop Type") +
  theme_minimal() +
  facet_wrap(~GEO)
```
</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>total Cultivated area</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
# Summarize production by year and crop type
# Plot the data
ggplot(total_produ, aes(x = REF_DATE, y = Production, color = Crop_Type)) +
  geom_line() +
  geom_point() +
    scale_color_manual(values = base_colors) +
  labs(title = "Total Production (metric tonnes) over Time",
       x = "Year",
       y = "Total Production",
       color = "Crop Type") +
  theme_minimal() +
  facet_wrap(~GEO)
```

</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>4.2:fruits data</b>
</h2>
<div style="display:none;">  




</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>year range</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
fruit_year <- data_statcan_fruit %>%
  group_by(Estimates,Crop_Type) %>%
  summarize(Start_Year = min(REF_DATE), End_Year = max(REF_DATE))
#order by Start_Year
fruit_year <- fruit_year[order(fruit_year$Start_Year),]
print(fruit_year,n = Inf, width = Inf)
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Yield (kilograms per hectare)</b>
</h4>
<div style="display:none;">  


```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

# Summarize production by year and crop type
# Plot the data
# Define the base colors
base_colors <- c('#0000FF', '#008000', '#FF0000', '#000000', '#FF00FF', 
                 '#FFA500', '#D2B48C', '#808000', 
                 '#FFFF00', 
                 '#40E0D0', '#00BFFF', '#A52A2A',
                 '#8A2BE2')
#drop na
full_fruits_yield_plot <- full_fruits %>%
  filter(!is.na(Yield_kg_per_ha)) 
ggplot(full_fruits_yield_plot, aes(x = Year, y = Yield_kg_per_ha, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Yield (kilograms per hectare) of Crops over Time",
       x = "Year",
       y = "Yield",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(min(full_fruits$Year), max(full_fruits$Year), by = 1))+
   scale_color_manual(values = base_colors)



# Plot the data
# ggplot(data_statcan_fruit_zoomed, aes(x = REF_DATE, y = Production, color = Crop_Type)) +
#   geom_line() +
#   geom_point() +
#   labs(title = "Production of Crops over Time",
#        x = "Year",
#        y = "Production",
#        color = "Crop Type") +
#   theme_minimal() 
```
</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Marketed production (ton)</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

ggplot(full_fruits, aes(x = Year, y = Production_Tons, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Yield (kilograms per hectare) of Crops over Time",
       x = "Year",
       y = "Yield",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(min(full_fruits$Year), max(full_fruits$Year), by = 5))+
   scale_color_manual(values = base_colors)
```



</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>total Cultivated area (Hectares)</b>
</h4>
<div style="display:none;">  


```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

ggplot(full_fruits_yield_plot, aes(x = Year, y = Area_Hectares, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Cultivated area (Hectares) of Crops over Time",
       x = "Year",
       y = "Area",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(min(full_fruits$Year), max(full_fruits$Year), by = 1))+
   scale_color_manual(values = base_colors)

full_fruits_zoom_area <- full_fruits %>%
   filter(Area_Hectares <= 3000)
ggplot(full_fruits_zoom_area, aes(x = Year, y = Area_Hectares, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Cultivated area (Hectares) of Crops over Time",
       x = "Year",
       y = "Area",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(min(full_fruits$Year), max(full_fruits$Year), by = 1))+
   scale_color_manual(values = base_colors)

fruits_zoom_more <- full_fruits %>%
   filter(Area_Hectares <= 1000)
ggplot(fruits_zoom_more, aes(x = Year, y = Area_Hectares, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Cultivated area (Hectares) of Crops over Time",
       x = "Year",
       y = "Area",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(min(full_fruits$Year), max(full_fruits$Year), by = 1))+
   scale_color_manual(values = base_colors)
```

## filter some fruits types
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
extend_fruits <- full_fruits %>%
   filter(Crop_Type == "plums and prune plums" | Crop_Type == "pears" | Crop_Type == "nectarines" | Crop_Type == "sour cherries" | Crop_Type == "strawberries" | Crop_Type == "peaches" | Crop_Type == "apricots") %>%
  filter(Year >= 2002)

#plot
ggplot(extend_fruits, aes(x = Year, y = Area_Hectares, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  labs(title = "Cultivated area (Hectares) of Crops over Time",
       x = "Year",
       y = "Area",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(2002, max(full_fruits$Year), by = 1))

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>fill area with mean </b>
</h3>
<div style="display:none;">  
#### mean as previous value
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
# Calculate the mean area for each crop type
# Calculate mean areas by Crop_Type
mean_areas <- full_fruits %>%
  group_by(Crop_Type) %>%
  summarize(Mean_Area = mean(Area_Hectares, na.rm = TRUE))

# Fill NA values in full_fruits$Area_Hectares with the corresponding mean
full_fruits_filled <- full_fruits %>%
  left_join(mean_areas, by = "Crop_Type") %>%
  mutate(Area_Hectares = ifelse(is.na(Area_Hectares), Mean_Area, Area_Hectares)) %>%
  select(-Mean_Area) # Remove the Mean_Area column if not needed

# Now you can proceed with your plotting or any other analysis
ggplot(full_fruits_filled, aes(x = Year, y = Area_Hectares, color = Crop_Type)) +
  geom_line() +
  theme_minimal()

```

#### calculate the yield again
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
full_fruits_filled$Yield_kg_per_ha <- full_fruits_filled$Production_Kg / full_fruits_filled$Area_Hectares


# Summarize production by year and crop type

ggplot(full_fruits_filled, aes(x = Year, y = Yield_kg_per_ha, color = Crop_Type)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = 2001, linetype = "dashed",color = "red") +
  labs(title = "Yield (kilograms per hectare) of Crops over Time",
       x = "Year",
       y = "Yield",
       color = "Crop Type") +
  theme_minimal()+
  scale_x_continuous(breaks = seq(min(full_fruits$Year), max(full_fruits$Year), by = 5))+
  scale_color_manual(values = base_colors)



```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>individual crop yield</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
for (i in unique(full_fruits_filled$Crop_Type)){
  p <- ggplot(full_fruits_filled %>% filter(Crop_Type == i), aes(x = Year, y = Yield_kg_per_ha)) +
    geom_line() +
    geom_point() +
      geom_vline(xintercept = 2001, linetype = "dashed",color = "red") +
    labs(title = paste("Yield of Crops over Time for", i),
         x = "Year",
         y = "Yield",
         color = "Crop Type") +
    theme_minimal() 
  print(p)
}

```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
# Summarize production by year and crop type
# Plot the data

#filter REF_DATE to 2011-2019
# data_statcan_fruit_com <- data_statcan_fruit %>%
#   filter(REF_DATE >= "2011" & REF_DATE <= "2019")
# 
# ggplot(data_statcan_fruit_com, aes(x = REF_DATE, y = Production, color  = interaction(Estimates, Crop_Type))) +
#   geom_line() +
#   geom_point() +
#   labs(title = "Production of Crops over Time",
#        x = "Year",
#        y = "Production",
#        color = "Crop Type") +
#   theme_minimal() 
# 
# #filter Production less than 15000
# data_statcan_fruit_less <- data_statcan_fruit_com %>%
#   filter(Production <= 15000)
# 
# #for loop of Crop_Type to plot
# for (i in unique(data_statcan_fruit_less$Crop_Type)){
#   p <- ggplot(data_statcan_fruit_less %>% filter(Crop_Type == i), aes(x = REF_DATE, y = Production, color  = (Estimates))) +
#     geom_line() +
#     geom_point() +
#     labs(title = paste("Production of Crops over Time for", i),
#          x = "Year",
#          y = "Production",
#          color = "Crop Type") +
#     theme_minimal() 
#   print(p)
# }
# 
# 
# 
# #filter Production less than 15000
# data_statcan_fruit_more <- data_statcan_fruit_com %>%
#   filter(Production > 10000)
# ggplot(data_statcan_fruit_more , aes(x = REF_DATE, y = Production,  color  = interaction(Estimates, Crop_Type))) +
#     geom_line() +
#     geom_point() +
#     labs(title = paste("Production of Crops over Time"),
#          x = "Year",
#          y = "Production",
#          color = "Crop Type") +
#     theme_minimal() 

```


</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>4.3: lm with crop 1990-2024</b>
</h2>
<div style="display:none;">  

</div>

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> FortStJohn monthly for Peace River region</b>
</h4>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage:
results <- perform_lm_monthly_statcan(monthly_data_x, crop_yield,"FortStJoh", "maxmon_EHF_95","Peace River, 8 - British Columbia")
#crop_yield
unique_crops <- unique(crop_yield$Crop_Type)
#Print results for each crop
for (crop in unique_crops) {
  print(paste("Results for crop:", crop))
  print(results[[crop]]$summary)
  if (!is.null(results[[crop]]$plot)) {
    print(results[[crop]]$plot)
  }
  
  
  
}

```


</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Part 5: veg data</b>
</h1>
<div style="display:none;">  



```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

veg_year
veg_year_2
# Use the functions
long_data <- process_data(data_veg_1940,"green peas")

# Define custom colors
custom_colors <- c(
  "Average_yield_per_acre_pounds" = "red",
  "Average_yield_per_hectare_kilograms" = "blue",
  "yield_tp_ah_acre_pounds" = "#008000",
  "yield_tp_ah_hectare_kg" = "#FF00FF",
  "yield_mp_ap_acre_pounds" = "#FFFF00",
  "yield_mp_ap_hectare_kg" = "#A52A2A",
  "yield_mp_ah_acre_pounds" = "#696969",
  "yield_mp_ah_hectare_kg" = "#40E0D0",
  "yield_tp_ap_acre_pounds" = "#FF1493",
  "yield_tp_ap_hectare_kg" = "#1E90FF"
)
# Plot all yields
plot_yields(long_data, custom_colors)

# Plot selected yields
selected_yield_types <- c("Average_yield_per_acre_pounds", "yield_mp_ah_hectare_kg", "yield_tp_ap_acre_pounds","yield_mp_ah_acre_pounds","yield_tp_ap_hectare_kg")
plot_selected_yields(long_data, selected_yield_types, custom_colors)




```


```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}

# data_veg_1940
# 
# veg_year_2
# unique(data_veg_1940$Crop_Type)
```
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=4}
#plot data_veg_1940 yield for diff type of veg
#each type is a plot

#check the rest crop yield is good

# data_veg_1940_yield <- data_veg_1940 %>%
#   filter(Estimates == "Average yield per acre (pounds)")
# for (i in unique(data_veg_1940_yield$Crop_Type)){
#   p <- ggplot(data_veg_1940_yield %>% filter(Crop_Type == i), aes(x = REF_DATE, y = VALUE)) +
#     geom_line() +
#     geom_point() +
#     labs(title = paste("Yield of Crops over Time for", i),
#          x = "Year",
#          y = "Yield",
#          color = "Crop Type") +
#     theme_minimal() 
#   print(p)
# }

```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=17, fig.height=9}
complete_data <- handle_missing_yield(data_veg_1940,crop_type = "asparagus")##green peas
backup_yield <- prepare_backup_yield(data_veg_1940)
merged_yield <- merge(complete_data, backup_yield, by = c("REF_DATE", "Crop_Type"), all.x = TRUE, suffixes = c("_Production", "_Area"))

plot_yield_over_time(merged_yield)

```




