---
title: "generalized extreme value (GEV) distribution for single variable "
author: "alex lin "
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---


<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>



```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R_model/GEV example (1)/gev.R") 
source("../R_model/read_data.R") 
source("../R_model/GEV_model.R") 

```


<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>GEV for single variable</b>
</h1>
<div style="display:none;">  

</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>FortNelson</b>
</h2>
<div style="display:none;">  


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>maxEHF</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}

plots <- gev_analysis_plots(ehf_ymax_wide, "fn","Annual MAX EHF")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> avgexc</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(avgexc_ymax_wide, "fn","Annual MAX Avg Exc Temp")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> total precipitation</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
load("../output/Rdata/FortNelson_imputed.RData")
#aggregate monthly precipitation
fn_imputed_month_prec <- FortNelson_imputed %>% select(year,month, totprec) %>% group_by(year,month) %>% summarise(totprec = sum(totprec,na.rm = TRUE))
fn_imputed_month_prec$station <- "fn"
fn_oct_prec <- fn_imputed_month_prec %>% filter(month == 10)

tot_prec_oct_wide <- fn_oct_prec %>% select(year,totprec) %>% rename(fn = totprec)

#load other station data
load("../output/Rdata/Abbotsford_imputed.RData")
load("../output/Rdata/Kelowna_imputed.RData")
load("../output/Rdata/Prince_George_imputed.RData")
load("../output/Rdata/YVR_imputed.RData")

ab_imputed_month_prec <- Abbotsford_imputed %>% select(year,month, totprec) %>% group_by(year,month) %>% summarise(totprec = sum(totprec,na.rm = TRUE))
ab_imputed_month_prec$station <- "ab"
ab_oct_prec <- ab_imputed_month_prec %>% filter(month == 10)

ke_imputed_month_prec <- Kelowna_imputed %>% select(year,month, totprec) %>% group_by(year,month) %>% summarise(totprec = sum(totprec,na.rm = TRUE))
ke_imputed_month_prec$station <- "ke"
ke_oct_prec <- ke_imputed_month_prec %>% filter(month == 10)

pg_imputed_month_prec <- Prince_George_imputed %>% select(year,month, totprec) %>% group_by(year,month) %>% summarise(totprec = sum(totprec,na.rm = TRUE))
pg_imputed_month_prec$station <- "pg"
pg_oct_prec <- pg_imputed_month_prec %>% filter(month == 10)

yv_imputed_month_prec <- YVR_imputed %>% select(year,month, totprec) %>% group_by(year,month) %>% summarise(totprec = sum(totprec,na.rm = TRUE))
yv_imputed_month_prec$station <- "yv"
yv_oct_prec <- yv_imputed_month_prec %>% filter(month == 10)

#merge all station data into tot_prec_oct_wide
#filter the column to only year and total precipitation
ab_oct_prec_merge <- ab_oct_prec %>% select(year,totprec) %>% rename(ab = totprec)
ke_oct_prec_merge <- ke_oct_prec %>% select(year,totprec) %>% rename(ke = totprec)
pg_oct_prec_merge <- pg_oct_prec %>% select(year,totprec) %>% rename(pg = totprec)
yv_oct_prec_merge <- yv_oct_prec %>% select(year,totprec) %>% rename(yv = totprec)


tot_prec_oct_wide <- merge(tot_prec_oct_wide, ab_oct_prec_merge, by = "year", all = TRUE)
tot_prec_oct_wide <- merge(tot_prec_oct_wide, ke_oct_prec_merge, by = "year", all = TRUE)
tot_prec_oct_wide <- merge(tot_prec_oct_wide, pg_oct_prec_merge, by = "year", all = TRUE)
tot_prec_oct_wide <- merge(tot_prec_oct_wide, yv_oct_prec_merge, by = "year", all = TRUE)

#need to look into why pg not from 1937!!
tot_prec_oct_wide_nonna <- tot_prec_oct_wide %>% filter(!is.na(fn) & !is.na(ab) & !is.na(ke) & !is.na(yv) & !is.na(pg))
plots <- gev_analysis_plots(tot_prec_oct_wide_nonna, "fn","Annual MAX Avg Exc Temp")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```
</div>


</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>YVR</b>
</h2>
<div style="display:none;">  


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Assess trend for EHF </b>
</h3>
<div style="display:none;">  

```{r echo=FALSE, message=FALSE, warning=FALSE}
# What are better methods to assess trend?
ehf0609 = read.csv("../R_model/GEV example (1)/ehf0609.csv", header=T)

# Create the plot
ggplot(ehf0609, aes(x = year, y = yv)) +
  geom_point() +  # Plot the data points
  geom_smooth(method = "lm", formula = y ~ I((x - 1941) / 10), color = "blue") +  # Add the linear regression line
  labs(title = "Trend of YV Over Years",
       x = "Year",
       y = "YV") +
  theme_minimal()
# Example: LOESS smoothing
library(ggplot2)
ggplot(ehf0609, aes(x=year, y=yv)) + 
  geom_point() + 
  geom_smooth(method="loess")
# Example: Seasonal Decomposition
library(forecast)
decomposed = stl(ts(ehf0609$yv, frequency=12), s.window="periodic")
plot(decomposed)
```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>maxEHF</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(ehf_ymax_wide, "yv","Annual MAX EHF")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> avgexc</b>
</h3>
<div style="display:none;"> 
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(avgexc_ymax_wide, "yv","Annual MAX Avg Exc Temp")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```



</div>

</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Kelowna</b>
</h2>
<div style="display:none;">  


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>maxEHF</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(ehf_ymax_wide, "ke","Annual MAX EHF")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> avgexc</b>
</h3>
<div style="display:none;"> 
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(avgexc_ymax_wide, "ke","Annual MAX Avg Exc Temp")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```



</div>

</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Abbotsford</b>
</h2>
<div style="display:none;">  


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>maxEHF</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(ehf_ymax_wide, "ab","Annual MAX EHF")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> avgexc</b>
</h3>
<div style="display:none;"> 
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(avgexc_ymax_wide, "ab","Annual MAX Avg Exc Temp")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```


</div>


</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Prince George</b>
</h2>
<div style="display:none;">  


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>maxEHF</b>
</h3>
<div style="display:none;">  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(ehf_ymax_wide, "pg","Annual MAX EHF")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> avgexc</b>
</h3>
<div style="display:none;"> 
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Example usage
plots <- gev_analysis_plots(avgexc_ymax_wide, "pg","Annual MAX Avg Exc Temp")
print(plots$qq_plot)
print(plots$return_level_plot)
print(plots$tail_behavior_plot)

```



