---
title: "Dry peroiods analysis"
author: "alex lin "
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---
<script>
function toggleCollapsible(section) {
  var content = section.nextElementSibling;
  if (content.style.display === "none") {
    content.style.display = "block";
  } else {
    content.style.display = "none";
  }
}
</script>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../drought_code_yvr/01-wrangle.r")  ## read data
source("../drought_code_yvr/02-90th.r")  ## data wrangling
source("../drought_code_yvr/03-heatdays.r")  ## heat wave analysis
source("../drought_code_yvr/04-exceedance.r")  ## heat wave analysis 2

source("../drought_code_yvr/05-dryperiods.r") ## dry periods analysis

source("../drought_code_yvr/06-diffwith90th.r") # Average difference with 90th by month,based on 1961-1990

source("../drought_code_yvr/07-5dayprecip.r") ## 5 day precipitation

source("../drought_code_yvr/08-drydays.r") 
source("../drought_code_yvr/09-plot.r")
source("../drought_code_yvr/diff_station_dry_cor.r") 
# start_year <- 1937
# end_year <- 2024
```


<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> Part 1: EDA</b>
</h1>
<div style="display:none;"> 




<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> YVR</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE,results = 'hide'}

# Call the function with the path to your CSV file
temp_precip_path<- process_data("../output/YVR_raw_filtered_columns.csv","YVR")

percentiles90th_path<- process_base_years(temp_precip_path,"YVR")


result_hw <- process_heat_periods(temp_precip_path, percentiles90th_path, "YVR")
# result_hw$q90_csv_path
# result_hw$heatwave_csv_path



```

```{r, echo=FALSE,warning=FALSE,message=FALSE}

# Extract dry periods
periods_dry_path <- extract_dry_periods(temp_precip_path, "YVR")


result_diff <- compute_avg_difference_90th(temp_precip_path, percentiles90th_path, "YVR")
result_diff$avg_exc_by_month
result_diff$diff_over_90th

max5d_precip_bymonth_path <- compute_cumulative_precip(temp_precip_path, "YVR")


```


```{r, echo=FALSE,warning=FALSE,message=FALSE}
imputed_temp_data <- impute_temps(temp_precip_path)
consec_precip_bymonth_path <- calculate_max_consec(imputed_temp_data, "YVR")
```


<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot nexc with year-month</b>
</h4>
<div style="display:none;">
```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_consecutive_dry_days(consec_precip_bymonth_path, start_year = 1940, end_year = 2024, step = 10)
```
</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Plot avg exc </b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=15, fig.height=6}
heatwave_csv_path_2 <- process_heat_exceedances(temp_precip_path, percentiles90th_path, "YVR")
heatwave_data <- read.csv(heatwave_csv_path_2)
plot_avg_temp_change(heatwave_data)
```






</div>
</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> Kelowna</b>
</h3>
<div style="display:none;"> 

```{r, echo=FALSE,warning=FALSE,message=FALSE}

# Call the function with the path to your CSV file
temp_precip_path<- process_data("../output/Kelowna_raw_filtered_columns.csv","Kelowna")

percentiles90th_path<- process_base_years(temp_precip_path,"Kelowna")

imputed_temp_data <- impute_temps(temp_precip_path)

consec_precip_bymonth_path_Kelowna <- calculate_max_consec(imputed_temp_data, "Kelowna")
```



<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot nexc with year-month</b>
</h4>
<div style="display:none;">  
#### Plot the consecutive dry days for Kelowna, starting from 1940, Kelowna has data from 1899 to 2024.
```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_consecutive_dry_days(consec_precip_bymonth_path_Kelowna, start_year = 1940, end_year = 2024, step = 10)

```



</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Plot avg exc </b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=15, fig.height=6}
heatwave_csv_path_2 <- process_heat_exceedances(temp_precip_path, percentiles90th_path, "Kelowna")
heatwave_data <- read.csv(heatwave_csv_path_2)
plot_avg_temp_change(heatwave_data)
```

</div>
</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> Prince George</b>
</h3>
<div style="display:none;"> 

```{r, echo=FALSE,warning=FALSE,message=FALSE}

# Call the function with the path to your CSV file
temp_precip_path<- process_data("../output/Prince_George_raw_filtered_columns.csv","Prince_George")
percentiles90th_path<- process_base_years(temp_precip_path,"Prince_George")

imputed_temp_data <- impute_temps(temp_precip_path)

consec_precip_bymonth_path_pg <- calculate_max_consec(imputed_temp_data, "Prince_George")
```


<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot nexc with year-month</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_consecutive_dry_days(consec_precip_bymonth_path_pg, start_year = 1940, end_year = 2024, step = 10)

```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Plot avg exc </b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=15, fig.height=6}
heatwave_csv_path_2 <- process_heat_exceedances(temp_precip_path, percentiles90th_path, "Prince_George")
heatwave_data <- read.csv(heatwave_csv_path_2)
plot_avg_temp_change(heatwave_data)
```

</div>
</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> FortNelson</b>
</h3>
<div style="display:none;"> 

```{r, echo=FALSE,warning=FALSE,message=FALSE}

# Call the function with the path to your CSV file
temp_precip_path<- process_data("../output/FortNelson_raw_filtered_columns.csv","FortNelson")
percentiles90th_path<- process_base_years(temp_precip_path,"FortNelson")

imputed_temp_data <- impute_temps(temp_precip_path)

consec_precip_bymonth_path_fn <- calculate_max_consec(imputed_temp_data, "FortNelson")

```


<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot nexc with year-month</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_consecutive_dry_days(consec_precip_bymonth_path_fn, start_year = 1940, end_year = 2024, step = 10)

```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Plot avg exc </b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=15, fig.height=6}
heatwave_csv_path_2 <- process_heat_exceedances(temp_precip_path, percentiles90th_path, "FortNelson")
heatwave_data <- read.csv(heatwave_csv_path_2)
plot_avg_temp_change(heatwave_data)
```

</div>
</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> Abbotsford</b>
</h3>
<div style="display:none;"> 

```{r, echo=FALSE,warning=FALSE,message=FALSE}

# Call the function with the path to your CSV file
temp_precip_path<- process_data("../output/Abbotsford_raw_filtered_columns.csv","Abbotsford")

percentiles90th_path<- process_base_years(temp_precip_path,"Abbotsford")

imputed_temp_data <- impute_temps(temp_precip_path)

consec_precip_bymonth_path_abb <- calculate_max_consec(imputed_temp_data, "Abbotsford")
```

<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b> plot nexc with year-month</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_consecutive_dry_days(consec_precip_bymonth_path_abb, start_year = 1940, end_year = 2024, step = 10)
dddedata <- read_csv(consec_precip_bymonth_path_abb)
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Plot avg exc </b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=15, fig.height=6}
heatwave_csv_path_2 <- process_heat_exceedances(temp_precip_path, percentiles90th_path, "Abbotsford")
heatwave_data <- read.csv(heatwave_csv_path_2)
plot_avg_temp_change(heatwave_data)
```



</div>
</div>
</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Part 2: Correlation </b>
</h1>
<div style="display:none;"> 


```{r, echo=FALSE,warning=FALSE,message=FALSE}
#consec_precip_bymonth_path_Kelowna
#plot_ccf_max_consec(consec_precip_bymonth_path_Kelowna,1899,"Kelowna",
#                    consec_precip_bymonth_path,1937,"YVR")
```



</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>scatter plot with top20 colored</b>
</h3>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
# Define the stations and their respective file paths and start years
stations <- list(
  Abbotsford = list(path = consec_precip_bymonth_path_abb, start_year = 1935),
  FortNelson = list(path = consec_precip_bymonth_path_fn, start_year = 1937),
  PrinceGeorge = list(path = consec_precip_bymonth_path_pg, start_year = 1940),
  Kelowna = list(path = consec_precip_bymonth_path_Kelowna, start_year = 1899),
  YVR = list(path = consec_precip_bymonth_path, start_year = 1937)
)

# Iterate over station pairs and generate scatter plots
station_names <- names(stations)
for (i in 1:(length(station_names) - 1)) {
  for (j in (i + 1):length(station_names)) {
    station1 <- station_names[i]
    station2 <- station_names[j]
    data_1_path <- stations[[station1]]$path
    data_2_path <- stations[[station2]]$path
    data1_start_year <- stations[[station1]]$start_year
    data2_start_year <- stations[[station2]]$start_year
    
    plot_scatter_color_top(data_1_path, data1_start_year, station1, data_2_path, data2_start_year, station2,1:19)
  }
}
```


</div>
<h1 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>Part 3: Ranking </b>
</h1>
<div style="display:none;">


</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>avgexc</b>
</h2>
<div style="display:none;">  

#### combine all station avgexc data
```{r, echo=FALSE,warning=FALSE,message=FALSE}
# Function to process data, base years, and heat exceedances for a station
process_station_data <- function(raw_data_path, station_name) {
  temp_precip_path <- process_data(raw_data_path, station_name)
  percentiles90th_path <- process_base_years(temp_precip_path, station_name)
  heatwave_csv_path <- process_heat_exceedances(temp_precip_path, percentiles90th_path, station_name)
  heatwave_data <- read.csv(heatwave_csv_path)
  heatwave_data$station <- station_name
  return(heatwave_data)
}

# List of stations and their corresponding raw data paths
stations_data <- list(
  "YVR" = "../output/YVR_raw_filtered_columns.csv",
  "Prince_George" = "../output/Prince_George_raw_filtered_columns.csv",
  "FortNelson" = "../output/FortNelson_raw_filtered_columns.csv",
  "Kelowna" = "../output/Kelowna_raw_filtered_columns.csv",
  "Abbotsford" = "../output/Abbotsford_raw_filtered_columns.csv"
)

# Initialize an empty list to hold data frames
all_heatwave_data <- list()

# Loop over each station, process data and store in the list
for (station in names(stations_data)) {
  raw_data_path <- stations_data[[station]]
  station_data <- process_station_data(raw_data_path, station)
  all_heatwave_data[[station]] <- station_data
}

# Combine all data frames into one
combined_heatwave_data <- do.call(rbind, all_heatwave_data)

#filter the year to be >= 1940
combined_heatwave_data <- combined_heatwave_data[combined_heatwave_data$year >= 1940, ]


# Save the combined data to a CSV file if needed
write.csv(combined_heatwave_data, "../drought_code_yvr/data/combined_avgexc.csv", row.names = FALSE)



```


<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>avgexc total year all stations scatter</b>
</h3>
<div style="display:none;">  

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=16, fig.height=6}

# Assuming combined_heatwave_data is the name of your dataframe
# Order data by avgexc
ordered_data <- combined_heatwave_data %>% arrange(desc(avgexc))

# Create a rank column within each station based on avgexc
ranked_data <- ordered_data %>%
  group_by(station) %>%
  mutate(rank = rank(-avgexc, ties.method = "first")) %>%
  ungroup()

# Convert rank to numeric type
ranked_data$rank <- as.numeric(as.character(ranked_data$rank))
#year-month column
ranked_data$yrmon <- as.Date(paste0(ranked_data$year, "-", ranked_data$month, "-01"))

#first 20 rows of ranked_data
head(ranked_data, 30)

station_colors <- c("Kelowna" = "red", "Prince_George" = "green", "YVR" = "blue",
                    "FortNelson" = '#FFD700', 'Abbotsford' = '#FF00FF')

# Scatter plot of avgexc vs. year
ggplot(ranked_data, aes(x = year, y = avgexc, color = station, size = rank)) +
  geom_point(alpha = 0.6) +
  labs(title = "Average Excess Temperature Over Years by Station",
       x = "Year",
       y = "Average Excess Temperature (°C)",
       size = "Rank") +
  theme_minimal()+
  #color
  scale_color_manual(values = station_colors) +
  scale_size_continuous(
    name = "Rank",
    trans = scales::trans_new(
      name = "custom",
      transform = function(x) ifelse(x > 100, 100, x),
      inverse = function(x) x,
      domain = c(0, 100)
    ),
    range = c(4, 1),  # Adjust this range based on the desired size scale
    limits = c(1, 100))+
  scale_x_continuous(breaks = seq(1940, 2024, by = 2))





# scatter plot, but x is year-month
# Scatter plot of avgexc vs. year
ggplot(ranked_data, aes(x = yrmon, y = avgexc, color = station, size = rank)) +
  geom_point(alpha = 0.6) +
  labs(title = "Average Excess Temperature Over Years by Station",
       x = "Year",
       y = "Average Excess Temperature (°C)",
       size = "Rank") +
  theme_minimal()+
  #color
  scale_color_manual(values = station_colors) +
  scale_size_continuous(
    name = "Rank",
    trans = scales::trans_new(
      name = "custom",
      transform = function(x) ifelse(x > 100, 100, x),
      inverse = function(x) x,
      domain = c(0, 100)
    ),
    range = c(4, 1),  # Adjust this range based on the desired size scale
    limits = c(1, 100))+
  #year-month scale
  scale_x_date(date_labels = "%Y", date_breaks = "2 year")

```


</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>avgexc SUMMER all stations scatter</b>
</h3>
<div style="display:none;">  

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=16, fig.height=6}
# filter month

ordered_data_summer <- ordered_data %>% filter(month %in% 6:9)
# Create a rank column within each station based on avgexc
ranked_data_summer <- ordered_data_summer %>%
  group_by(station) %>%
  mutate(rank = rank(-avgexc, ties.method = "first")) %>%
  ungroup()

# Convert rank to numeric type
ranked_data_summer$rank <- as.numeric(as.character(ranked_data_summer$rank))
#year-month column
ranked_data_summer$yrmon <- as.Date(paste0(ranked_data_summer$year, "-", ranked_data_summer$month, "-01"))



ggplot(ranked_data_summer, aes(x = yrmon, y = avgexc, color = station, size = rank)) +
  geom_point(alpha = 0.6) +
  geom_text(aes(label = ifelse(rank <= 15, rank, "")), vjust = -0.5, size = 3, color = "black") +  # Add rank labels for top 20
  labs(title = "Average Excess Temperature June-Sep by Station",
       x = "Year",
       y = "Average Excess Temperature (°C)",
       size = "Rank") +
  theme_minimal()+
  #color
  scale_color_manual(values = station_colors) +
  scale_size_continuous(
    name = "Rank",
    trans = scales::trans_new(
      name = "custom",
      transform = function(x) ifelse(x > 100, 100, x),
      inverse = function(x) x,
      domain = c(0, 100)
    ),
    range = c(6, 1),  # Adjust this range based on the desired size scale
    limits = c(1, 100))+
  #year-month scale
  scale_x_date(date_labels = "%Y", date_breaks = "2 year")
```

</div>
<h3 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>avgexc for specific year</b>
</h3>
<div style="display:none;">  

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>1941</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
#fliter the year
ranked_data_1941 <- ranked_data_summer %>% filter(year == 1941)
#ranked_data_1941
#2021
ranked_data_2021 <- ranked_data_summer %>% filter(year == 2021)
#ranked_data_2021
```



```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_avg_exc_temp(ranked_data_1941,1941)
  
```

</div>
<h4 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>2021</b>
</h4>
<div style="display:none;">  
```{r, echo=FALSE,warning=FALSE,message=FALSE}
plot_avg_exc_temp(ranked_data_2021, 2021)
```


```{r, echo=FALSE,warning=FALSE,message=FALSE}
# Apply the function to your datasets





```

</div>

</div>
<h2 onclick="toggleCollapsible(this);">
<!--TEXT SHOWS: -->
<b>max_consec</b>
</h2>
<div style="display:none;">  

```{r, echo=FALSE,warning=FALSE,message=FALSE}
# Define the stations and their respective file paths and start years
stations <- list(
  Abbotsford = list(path = consec_precip_bymonth_path_abb, start_year = 1935),
  FortNelson = list(path = consec_precip_bymonth_path_fn, start_year = 1937),
  PrinceGeorge = list(path = consec_precip_bymonth_path_pg, start_year = 1940),
  Kelowna = list(path = consec_precip_bymonth_path_Kelowna, start_year = 1899),
  YVR = list(path = consec_precip_bymonth_path, start_year = 1937)
)

# Initialize an empty list to store data frames
data_list <- list()

# Iterate over stations to read and combine data
for (station in names(stations)) {
  data_path <- stations[[station]]$path
  data <- read.csv(data_path)  # Adjust the reading function if the data is not in CSV format
  data$Station <- station
  data_list[[station]] <- data
}

# Combine all data frames into one
combined_data_consec <- do.call(rbind, data_list)

# create new column year and month based on yrmon
combined_data_consec$year <- as.integer(substr(combined_data_consec$yrmon, 1, 4))
combined_data_consec$month <- as.integer(substr(combined_data_consec$yrmon, 5, 6))

# Save the combined data frame to a file
write.csv(combined_data_consec, "../drought_code_yvr/data/combine_max_consec.csv", row.names = FALSE)
```
#### Rank the stations based on the number of dry days

```{r, echo=FALSE,warning=FALSE,message=FALSE}


```





